---
title: "BioAge_HealthyUnhealthy_Merge_5.0.Rmd"
output: html_document
date: "2023-08-21"
---

This file reads in the blood-based biomarker (BBB) data and merges it with healthy and unhealthy participants. Also merges demographic data.

1. Merge CBCL and PhysHealth to determine healthy and unhealthy
2. Merge healthy and unhealthy data frame with BBB
3. Merge demographic data
4. Output data frame ready for training and testing.


# Libraries
```{r, warning=FALSE, error = FALSE, message=FALSE}
library(BioAge)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(stats)
library(skimr)
library(stringr)
library(devtools)
library(tidyr)
library(reshape2)
```


# Read in Data
```{r}
# Read in CBCL
p_cbcl_t <- read.csv(paste0(root, "Version5.0_Exported_Data/p_cbcl_t.csv"))

# Child medical history
mhx <- read.csv(paste0(root,"Version5.0_Exported_Data/mhx.csv"))

# Read in BBB
bbb <- read.csv(paste0(root, "Version5.0_Exported_Data/biomarkers_5.csv"))
bbb %>% filter(eventname == "2_year_follow_up_y_arm_1")

# Longitudinal Demographic data
long_dem <- read.csv(paste0(root, "abcd-data-release-5.0/core/abcd-general/abcd_y_lt.csv"))

# Data on gender
gender_y <- read.csv(paste0(root, "abcd-data-release-5.0/core/gender-identity-sexual-health/gish_y_gi.csv"))

gender_p <- read.csv(paste0(root, "abcd-data-release-5.0/core/gender-identity-sexual-health/gish_p_gi.csv"))

gender_a <- read.csv(paste0(root, "abcd-data-release-5.0/core/abcd-general/abcd_p_demo.csv"))
```


# Merge mhx and p_cbcl_t
## Baseline
```{r}
phys_ment <- merge(p_cbcl_t, mhx, by = c("src_subject_id", "eventname"))
phys_ment <- phys_ment %>%
  rename(ment_health = cbcl_tot, phys_health = tot_prob)

# add a column that adds ment_health + phys_health
table(phys_ment %>% filter(eventname == "baseline_year_1_arm_1") %>% select(phys_health))
table(phys_ment %>% filter(eventname == "baseline_year_1_arm_1") %>% select(ment_health))

phys_ment <- phys_ment %>%
  mutate(phys_ment_health = ment_health + phys_health)


# Distribution of physical or mental health problems at baseline
table(phys_ment %>% filter(eventname == "2_year_follow_up_y_arm_1") %>% select(phys_ment_health))

# Number of unique participants with physical and mental health info
table(phys_ment$eventname)
```

# Merge phys_ment with bbb
```{r}
dim(bbb)
bbb_healthy <- merge(bbb, 
                     phys_ment %>% 
                       filter(phys_ment_health == 0) %>%
                       select(src_subject_id, eventname, ment_health, phys_health, phys_ment_health),
                     by = c("src_subject_id", "eventname"))

bbb_healthy %>% filter(eventname == "2_year_follow_up_y_arm_1")

bbb_unhealthy <- merge(bbb, 
                     phys_ment %>% 
                       filter(phys_ment_health > 0) %>%
                       select(src_subject_id, eventname, ment_health, phys_health, phys_ment_health),
                     by = c("src_subject_id", "eventname"))

bbb_unhealthy %>% filter(eventname == "2_year_follow_up_y_arm_1")

```

# Merge Demographic Data
*** V.5.1 - Already did in initial.rmd
```{r}
# dem <- merge(gender_p %>% select(src_subject_id, eventname, demo_sex_v2), 
#       long_dem %>% select(src_subject_id, eventname, site_id_l, rel_family_id, interview_age), 
#       by = c("src_subject_id", "eventname"))
# 
# # Create Sex Column
# dem <- dem %>%
#   group_by(src_subject_id) %>%
#   mutate(
#     sex = ifelse(any(demo_sex_v2 == 1, na.rm = TRUE), ifelse(is.na(demo_sex_v2), 1, demo_sex_v2),
#            ifelse(any(demo_sex_v2 == 2, na.rm = TRUE), ifelse(is.na(demo_sex_v2), 2, demo_sex_v2), demo_sex_v2))
#   ) %>%
#   ungroup()
# 
# # Add column for rel_family_id that does the same as the above for sex
# dem <- dem %>%
#   group_by(src_subject_id) %>%
#   mutate(
#     rel_family_id = ifelse(all(is.na(rel_family_id)), NA, first(rel_family_id[!is.na(rel_family_id)]))
#   ) %>%
#   ungroup()




# Merge with healthy BBB
bbb_healthy_dem <- bbb_healthy

# Merge with unhealthy BBB
bbb_unhealthy_dem <- bbb_unhealthy

```


# Clean each dataframe
```{r}
# Remove some unnecessary columns
# bbb_healthy_dem <- bbb_healthy_dem %>% select(-c(X, demo_sex_v2))
bbb_healthy_dem <- bbb_healthy_dem %>% select(-ends_with(".y"))
# bbb_unhealthy_dem <- bbb_unhealthy_dem %>% select(-c(X, demo_sex_v2))
bbb_unhealthy_dem <- bbb_unhealthy_dem %>% select(-ends_with(".y"))

# Rename columns ending with ".x" to the same column without ".x"
bbb_healthy_dem <- bbb_healthy_dem %>%
  rename_all(~ gsub("\\.x$", "", .))
bbb_unhealthy_dem <- bbb_unhealthy_dem %>%
  rename_all(~ gsub("\\.x$", "", .))

# Add age column
bbb_healthy_dem$age <- (bbb_healthy_dem$interview_age) / 12
bbb_unhealthy_dem$age <- (bbb_unhealthy_dem$interview_age) / 12

```


# Split into Time points BBB
```{r}

# Baseline
bbb_healthy_dem_2year <- bbb_healthy_dem %>% filter(eventname == "2_year_follow_up_y_arm_1")
bbb_unhealthy_dem_2year <- bbb_unhealthy_dem %>% filter(eventname == "2_year_follow_up_y_arm_1")

# Year 2
bbb_healthy_dem_3year <- bbb_healthy_dem %>% filter(eventname == "3_year_follow_up_y_arm_1")
bbb_unhealthy_dem_3year <- bbb_unhealthy_dem %>% filter(eventname == "3_year_follow_up_y_arm_1")

# Year 4
bbb_healthy_dem_4year <- bbb_healthy_dem %>% filter(eventname == "4_year_follow_up_y_arm_1")
bbb_unhealthy_dem_4year <- bbb_unhealthy_dem %>% filter(eventname == "4_year_follow_up_y_arm_1")

bbb_2year <- rbind(bbb_healthy_dem_2year, bbb_unhealthy_dem_2year)
bbb_3year <- rbind(bbb_healthy_dem_3year, bbb_unhealthy_dem_3year)
bbb_4year <- rbind(bbb_healthy_dem_4year, bbb_unhealthy_dem_4year)

```


# Export
```{r}
write.csv(bbb_2year, paste0(root, "Version5.0_Exported_Data/bbb_2year.csv"))
write.csv(bbb_3year, paste0(root, "Version5.0_Exported_Data/bbb_3year.csv"))
write.csv(bbb_4year, paste0(root, "Version5.0_Exported_Data/bbb_4year.csv"))


```














