---
title: "BrainAge_HealthyUnhealthy_Merge_5.0"
output: html_document
date: "2023-07-18"
---

This file merges the GMV and Cortical Thickness data with healthy and unhealthy participants. Also merges demographic data.

1. Merge CBCL and PhysHealth to determine healthy and unhealthy
2. Merge healthy and unhealthy data frame with GMV
3. Merge demographic data
4. Output data frame ready for training and testing.


# Libraries
```{r, warning=FALSE, error = FALSE, message=FALSE}
library(BioAge)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(stats)
library(skimr)
library(stringr)
library(devtools)
library(tidyr)
library(reshape2)
```


# Read in Data
```{r}
# Read in CBCL
p_cbcl_t <- read.csv(paste0(root, "Version5.0_Exported_Data/p_cbcl_t.csv"))

# Child medical history
mhx <- read.csv(paste0(root,"Version5.0_Exported_Data/mhx.csv"))

# Read in GMV
gmv <- read.csv(paste0(root, "Version5.0_Exported_Data/smri_5_gvol_all_qc.csv"))

# Read in Cort thick data
thk <- read.csv(paste0(root, "Version5.0_Exported_Data/smri_5_thick_qc.csv"))

# Longitudinal Demographic data
long_dem <- read.csv(paste0(root, "abcd-data-release-5.1/core/abcd-general/abcd_y_lt.csv"))

# Data on gender
gender_y <- read.csv(paste0(root, "abcd-data-release-5.1/core/gender-identity-sexual-health/gish_y_gi.csv"))

gender_p <- read.csv(paste0(root, "abcd-data-release-5.1/core/gender-identity-sexual-health/gish_p_gi.csv"))

gender_a <- read.csv(paste0(root, "abcd-data-release-5.1/core/abcd-general/abcd_p_demo.csv"))


nrow(p_cbcl_t %>% filter(eventname == "baseline_year_1_arm_1"))
nrow(mhx %>% filter(eventname == "baseline_year_1_arm_1"))
nrow(gmv %>% filter(eventname == "baseline_year_1_arm_1"))
nrow(long_dem %>% filter(eventname == "baseline_year_1_arm_1"))
nrow(gender %>% filter(eventname == "baseline_year_1_arm_1"))
```


# Merge mhx and p_cbcl_t
## Baseline
```{r}
phys_ment <- merge(p_cbcl_t, mhx, by = c("src_subject_id", "eventname"))

phys_ment <- phys_ment %>%
  rename(tot_prob_phys = tot_prob)

# add a column that adds ment_health + phys_health
table(phys_ment %>% filter(eventname == "baseline_year_1_arm_1") %>% select(cbcl_tot))
table(phys_ment %>% filter(eventname == "baseline_year_1_arm_1") %>% select(tot_prob_phys))

# Ordinal
phys_ment <- phys_ment %>%
  mutate(phys_ment_health = cbcl_tot + tot_prob_phys)

# Binary
phys_ment$phys_ment_health_bin <- ifelse(phys_ment$phys_ment_health > 0, 1, 0)

# Distribution of physical or mental health problems at baseline
table(phys_ment %>% filter(eventname == "baseline_year_1_arm_1") %>% select(phys_ment_health))
table(phys_ment %>% filter(eventname == "baseline_year_1_arm_1") %>% select(phys_ment_health_bin))

# Number of unique participants with physical and mental health info
table(phys_ment$eventname)

write.csv(phys_ment, paste0(root, "Version5.0_Exported_Data/phys_ment.csv"))

```
More "unhealthy" than healthy. Many children with physical problems (mostly high fever)
IMPORTANT: Only 4671 at 4 year follow up, but we don't need this time point. We only need baseline for calculating KDM. 


# Merge phys_ment with GMV
```{r}

gmv_healthy <- merge(gmv, 
                     phys_ment %>% 
                       filter(phys_ment_health_bin == 0) %>%
                       select(src_subject_id, eventname, cbcl_tot, 
                              phys_health_bin:phys_ment_health_bin),
                     by = c("src_subject_id", "eventname"))


nrow(gmv_healthy %>% filter(eventname == "baseline_year_1_arm_1"))

gmv_unhealthy <- merge(gmv, 
                     phys_ment %>% 
                       filter(phys_ment_health > 0) %>%
                       select(src_subject_id, eventname, cbcl_tot, 
                              phys_health_bin:phys_ment_health_bin),
                     by = c("src_subject_id", "eventname"))


nrow(gmv_unhealthy %>% filter(eventname == "baseline_year_1_arm_1"))




```

# Merge phys_ment with Cortical Thickness
```{r}
thk_healthy <- merge(thk, 
                     phys_ment %>% 
                       filter(phys_ment_health_bin == 0) %>%
                       select(src_subject_id, eventname, phys_health_bin:phys_ment_health_bin),
                     by = c("src_subject_id", "eventname"))

thk_unhealthy <- merge(thk, 
                     phys_ment %>% 
                       filter(phys_ment_health_bin > 0) %>%
                       select(src_subject_id, eventname, phys_health_bin:phys_ment_health_bin),
                     by = c("src_subject_id", "eventname"))


```


# Merge Demographic Data
```{r}
dem <- merge(gender_p %>% select(src_subject_id, eventname, demo_sex_v2), 
      long_dem %>% select(src_subject_id, eventname, site_id_l, rel_family_id, interview_age), 
      by = c("src_subject_id", "eventname"))

# Create Sex Column
dem <- dem %>%
  group_by(src_subject_id) %>%
  mutate(
    sex = ifelse(any(demo_sex_v2 == 1, na.rm = TRUE), ifelse(is.na(demo_sex_v2), 1, demo_sex_v2),
           ifelse(any(demo_sex_v2 == 2, na.rm = TRUE), ifelse(is.na(demo_sex_v2), 2, demo_sex_v2), demo_sex_v2))
  ) %>%
  ungroup()

# Add column for rel_family_id that does the same as the above for sex
dem <- dem %>%
  group_by(src_subject_id) %>%
  mutate(
    rel_family_id = ifelse(all(is.na(rel_family_id)), NA, first(rel_family_id[!is.na(rel_family_id)]))
  ) %>%
  ungroup()


# Merge with healthy GMV
gmv_healthy_dem <- merge(gmv_healthy, dem, by = c("src_subject_id", "eventname"))

# Merge with unhealthy GMV
gmv_unhealthy_dem <- merge(gmv_unhealthy, dem, by = c("src_subject_id", "eventname"))

# Merge with healthy Cortical Thickness
thk_healthy_dem <- merge(thk_healthy, dem, by = c("src_subject_id", "eventname"))

# Merge with unhealthy Cortical Thickness
thk_unhealthy_dem <- merge(thk_unhealthy, dem, by = c("src_subject_id", "eventname"))

```

# Clean each dataframe
```{r}

# clean_df <- function () {
#   # Get rid of 
#   
#     tryCatch(
#     {
#       # Try this:
#       as.numeric(x)
#     },
#     error = function(e) {
#       # If there's an error, do this instead:
#       message("Error occurred: ", e)
#       NA  # This value will be used in case of error
#     }
#   )
#   
# }
gmv_healthy_dem <- gmv_healthy_dem %>% select(-X) 
gmv_unhealthy_dem <- gmv_unhealthy_dem %>% select(-X)

# Add age column
gmv_healthy_dem$age <- (gmv_healthy_dem$interview_age) / 12
gmv_unhealthy_dem$age <- (gmv_unhealthy_dem$interview_age) / 12

thk_healthy_dem <- thk_healthy_dem %>% select(-X) 
thk_unhealthy_dem <- thk_unhealthy_dem %>% select(-X)

# Add age column
thk_healthy_dem$age <- (thk_healthy_dem$interview_age) / 12
thk_unhealthy_dem$age <- (thk_unhealthy_dem$interview_age) / 12

```

# Split into Time points GMV
```{r}
# Baseline
gmv_healthy_dem_base <- gmv_healthy_dem %>% filter(eventname == "baseline_year_1_arm_1")
gmv_unhealthy_dem_base <- gmv_unhealthy_dem %>% filter(eventname == "baseline_year_1_arm_1")

# Year 2
gmv_healthy_dem_2year <- gmv_healthy_dem %>% filter(eventname == "2_year_follow_up_y_arm_1")
gmv_unhealthy_dem_2year <- gmv_unhealthy_dem %>% filter(eventname == "2_year_follow_up_y_arm_1")

# Year 4
gmv_healthy_dem_4year <- gmv_healthy_dem %>% filter(eventname == "4_year_follow_up_y_arm_1")
gmv_unhealthy_dem_4year <- gmv_unhealthy_dem %>% filter(eventname == "4_year_follow_up_y_arm_1")


```

# Split into Time points Cortical Thickness
```{r}
# Baseline
thk_healthy_dem_base <- thk_healthy_dem %>% filter(eventname == "baseline_year_1_arm_1")
thk_unhealthy_dem_base <- thk_unhealthy_dem %>% filter(eventname == "baseline_year_1_arm_1")

# Year 2
thk_healthy_dem_2year <- thk_healthy_dem %>% filter(eventname == "2_year_follow_up_y_arm_1")
thk_unhealthy_dem_2year <- thk_unhealthy_dem %>% filter(eventname == "2_year_follow_up_y_arm_1")

# Year 4
thk_healthy_dem_4year <- thk_healthy_dem %>% filter(eventname == "4_year_follow_up_y_arm_1")
thk_unhealthy_dem_4year <- thk_unhealthy_dem %>% filter(eventname == "4_year_follow_up_y_arm_1")

```


# Standardize by Gender GMV
```{r}
# Standardize each region by gender
## NB: When scaling, it should only be by gender, not health
## Returns list of scaled male and female dataframes
# standardize <- function(healthy, unhealthy) {
#   gmv_forScale <- rbind(healthy, unhealthy)
# 
#   ## Males
#   gmv_forScale_male <- gmv_forScale %>% filter(sex == 1)
# 
#   gmv_forScale_male <- gmv_forScale_male %>%
#     mutate(across(starts_with("smri_vol_cdk_banksstslh"):ends_with("smri_vol_scs_subcorticalgv"), scale))
# 
#   ## Females
#   gmv_forScale_female <- gmv_forScale %>% filter(sex == 2)
#   
#   gmv_forScale_female <- gmv_forScale_female %>%
#     mutate(across(starts_with("smri_vol_cdk_banksstslh"):ends_with("smri_vol_scs_subcorticalgv"), scale))
#   
#   return(rbind(gmv_forScale_male, gmv_forScale_female))
# }

# gmv_base <- standardize(gmv_healthy_dem_base, gmv_unhealthy_dem_base)
# gmv_2year <- standardize(gmv_healthy_dem_2year, gmv_unhealthy_dem_2year)
# gmv_4year <- standardize(gmv_healthy_dem_4year, gmv_unhealthy_dem_4year)

gmv_base <- rbind(gmv_healthy_dem_base, gmv_unhealthy_dem_base)
gmv_2year <- rbind(gmv_healthy_dem_2year, gmv_unhealthy_dem_2year)
gmv_4year <- rbind(gmv_healthy_dem_4year, gmv_unhealthy_dem_4year)

smri_list <- colnames(gmv_base %>% select(contains("smri")))

for (smri in 1:length(smri_list)) {
  hist(gmv_base[, smri_list[smri]], xlab = smri_list[smri])
}
```


# Check Raw Values by Healthy and Unhealthy
```{r}

table(gmv_base$tot_prob_phys)
table(gmv_base$cbcl_tot)


gmv_base$group <- ifelse(gmv_base$phys_ment_health_bin > 0, "unhealthy", "healthy")
table(gmv_base$group)

smri_list <- colnames(gmv_base %>% select(contains("smri")))

for (smri in smri_list) {
  print(smri)
  
  print(
    ggplot(gmv_base %>% filter(sex == 2), aes_string(x = smri, y = "..density..", fill = "group", alpha = 0.5)) +
  geom_histogram(position = "identity", bins = 30) +
  theme_minimal() +
  labs(x = smri, y = "Frequency", fill = "group", title = "Overlaying Density Plots") +
  guides(alpha = FALSE)
  )
}
```


# Standardize by Gender Cortical Thickness
```{r}

# Standardize each region by gender
## NB: When scaling, it should only be by gender, not health
## Returns list of scaled male and female dataframes
# standardize <- function(healthy, unhealthy) {
#   thk_forScale <- rbind(healthy, unhealthy)
# 
#   ## Males
#   thk_forScale_male <- thk_forScale %>% filter(sex == 1)
# 
#   thk_forScale_male <- thk_forScale_male %>%
#     mutate(across(starts_with("smri_thick_cdk_banksstslh"):ends_with("smri_thick_cdk_mean"), scale))
# 
#   ## Females
#   thk_forScale_female <- thk_forScale %>% filter(sex == 2)
#   
#   thk_forScale_female <- thk_forScale_female %>%
#     mutate(across(starts_with("smri_thick_cdk_banksstslh"):ends_with("smri_thick_cdk_mean"), scale))
#   
#   return(rbind(thk_forScale_male, thk_forScale_female))
# }

thk_base <- rbind(thk_healthy_dem_base, thk_unhealthy_dem_base)
thk_2year <- rbind(thk_healthy_dem_2year, thk_unhealthy_dem_2year)
thk_4year <- rbind(thk_healthy_dem_4year, thk_unhealthy_dem_4year)

```


# Export
```{r}
gmv_base <- gmv_base %>% select(-group)

gmv_base$phys_ment_health

write.csv(gmv_base, paste0(root, "Version5.0_Exported_Data/gmv_base.csv"))
write.csv(gmv_2year, paste0(root, "Version5.0_Exported_Data/gmv_2year.csv"))
write.csv(gmv_4year, paste0(root, "Version5.0_Exported_Data/gmv_4year.csv"))

write.csv(thk_base, paste0(root, "Version5.0_Exported_Data/thk_base.csv"))
write.csv(thk_2year, paste0(root, "Version5.0_Exported_Data/thk_2year.csv"))
write.csv(thk_4year, paste0(root, "Version5.0_Exported_Data/thk_4year.csv"))

```







