---
title: "BrainAge_GMV_V5.0"
output: html_document
date: "2023-07-17"
---

This file reads in the GMV data necessary for a longitudinal analysis of Brain Age (Baseline, 2 year, 4 year). It also only includes values that pass the quality control threshold, and includes scanner information for use as a covariate. Also merges sex variable

NB: Will need to get sex variable from gish_y_gi file

# Libraries
```{r}
library(BioAge)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(stats)
library(skimr)
library(stringr)
library(devtools)
library(neuroCombat)
library(tidyr)
library(reshape2)
```


# Read in Data
```{r}
# sMRI GMV data
smri_5 <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/imaging/mri_y_smr_vol_dsk.csv")

# QC Recommended Image Inclusion
image_inc <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/imaging/mri_y_qc_incl.csv")

# Quality Control - Manual - Post-processing - Structural MRI - T2w
post_proc <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/imaging/mri_y_qc_incl.csv")

# Quality Control - Manual - Freesurfer
fsurf_qc <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/imaging/mri_y_qc_man_fsurf.csv")

# Longitudinal Demographic data
long_dem <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/abcd-general/abcd_y_lt.csv")

# Longitudinal Demographic data
mri_info <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/imaging/mri_y_adm_info.csv")

# Data on gender
gender <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/gender-identity-sexual-health/gish_y_gi.csv")


```


# Clean sMRI GMV Data and merge with subcortical file
```{r}
# GMV
# Select only cortical volume measures
# Make sure to not include white matter (ex. corpus callosum) or ventricles
smri_5_gvol <- smri_5 %>% select(c("src_subject_id", "eventname",
                                "smri_vol_cdk_banksstslh":"smri_vol_cdk_insularh", 
                            "smri_vol_cdk_totallh":"smri_vol_cdk_total"))

smri_5_gvol[smri_5_gvol == ""] <- NA
smri_5_gvol <- smri_5_gvol[complete.cases(smri_5_gvol), ]



# Subcortical GMV
smri_5_sub_vol <- smri_5_sub %>% select(c("src_subject_id", "eventname", 
                            "smri_vol_scs_crbcortexlh":"smri_vol_scs_pallidumlh",
                            "smri_vol_scs_hpuslh":"smri_vol_scs_amygdalalh", 
                            "smri_vol_scs_aal":"smri_vol_scs_vedclh", 
                            "smri_vol_scs_crbcortexrh":"smri_vol_scs_amygdalarh", 
                            "smri_vol_scs_aar":"smri_vol_scs_vedcrh", "smri_vol_scs_subcorticalgv"))
smri_5_sub_vol[smri_5_sub_vol == ""] <- NA
smri_5_sub_vol <- smri_5_sub_vol[complete.cases(smri_5_sub_vol), ]

smri_5_gvol_all <- merge(smri_5_gvol, smri_5_sub_vol, by = c("src_subject_id", "eventname"))

skim(smri_5_gvol_all) # 22854
```

# Quality Control for sMRI
## t1w is used to calculate volume
```{r}

all_qc <- merge(fsurf_qc %>% select(src_subject_id, eventname, fsqc_qc),
                post_proc %>% select(src_subject_id, eventname, imgincl_t1w_include),
                by = c("src_subject_id", "eventname"))

qc_remove <- all_qc %>% 
  filter(fsqc_qc == 0 | imgincl_t1w_include == 0) %>% 
  select(src_subject_id, eventname)

smri_5_gvol_all_qc <- anti_join(smri_5_gvol_all, qc_remove, by = c("src_subject_id", "eventname"))

```


# Convert sMRI values to numeric
```{r}
smri_5_gvol_all_qc <- smri_5_gvol_all_qc %>% 
  mutate_at(vars(contains("smri")), as.numeric)

smri_5_gvol_all_qc <- smri_5_gvol_all_qc[complete.cases(smri_5_gvol_all_qc), ]

skim(smri_5_gvol_all_qc) # 22197
```


# Check Distributions
Seems pretty clean
```{r}
smri_list <- colnames(smri_5_gvol_all_qc %>% select(contains("smri")))

for (smri in 1:length(smri_list)) {
  hist(smri_5_gvol_all_qc[, smri_list[smri]], xlab = smri_list[smri])
}



```

# Include MRI Manufacturer
```{r}
mri_info$mri_info_manufacturer <- as.factor(mri_info$mri_info_manufacturer)
smri_5_gvol_all_qc <- merge(smri_5_gvol_all_qc, 
                            mri_info %>% select(src_subject_id, eventname, mri_info_manufacturer), 
                            by = c("src_subject_id", "eventname"))

```


# Export
```{r}
write.csv(smri_5_gvol_all_qc, paste0(root, "Version5.0_Exported_Data/smri_5_gvol_all_qc.csv"))
head(smri_5_gvol_all_qc)
```

























