---
title: "BrainAge_FeatureSelection_5.0"
output: html_document
date: "2023-07-19"
---

This file performs feature selection for the GMV and Cortical Thickness ROIs necessary for Brain Age Prediction. Only the baseline values are needed since the model will be trained on the baseline data. Outputs the feature selected baseline dataframe as well as the feature selected dataframes at year 2 and year 4.

Input:
+ gmv_base.csv

Output:
+ gmv_sub_base.csv
+ gmv_sub_2year.csv
+ gmv_sub_4year.csv

# Library
```{r}
library(BioAge)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(stats)
library(skimr)
library(pcaPP)
library(corrr)
```


# Read in Data
```{r}
gmv_base <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_base.csv"))
gmv_2year <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_2year.csv"))
gmv_4year <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_4year.csv"))

thk_base <- read.csv(paste0(root, "Version5.0_Exported_Data/thk_base.csv"))
thk_2year <- read.csv(paste0(root, "Version5.0_Exported_Data/thk_2year.csv"))
thk_4year <- read.csv(paste0(root, "Version5.0_Exported_Data/thk_4year.csv"))

```

# Merge all together
```{r}
gmv_all <- rbind(gmv_base, rbind(gmv_2year, gmv_4year))
thk_all <- rbind(thk_base, rbind(thk_2year, thk_4year))

```



# Check the relationship between CA and ROIs as a table
## IMPORTANT: Kendall's Tau takes too long in regular cor() function. Use cor.fk from pcaPP package
```{r}
cor_mat_non_para <- function(df) {
  
  df$age <- as.numeric(df$interview_age)/12
  df <- df[complete.cases(df),]
  
  cor_sub <- df %>% dplyr::select(contains(c("smri", "age")))
  cor_sub <- cor_sub %>% dplyr::select(-interview_age)
  
  smri_list <- colnames(df %>% dplyr::select(contains("smri")))
  cor_matrix <- cor.fk(cor_sub)
  correlations <- cor_matrix["age", smri_list]
  
  # Matrix with highest absolute correlations between ROI and age
  cor_mat_kendall <- sort(abs(correlations), decreasing = T)
  
  # Convert to Pearson's r and Cohen's d for effect size comparison
  cor_mat_kendall_to_r <- sin(pi*0.5*cor_mat_kendall)
  cor_mat_kendall_to_d <- 2*cor_mat_kendall_to_r/sqrt(1-cor_mat_kendall_to_r**2)
  
  return(cor_mat_kendall_to_r)
}

```

# Check Correlations 
## GMV
```{r}

gmv_healthy <- gmv_all %>% 
  filter(phys_ment_health == 0) %>% 
  filter(eventname == "baseline_year_1_arm_1")
gmv_cors <- cor_mat_non_para(gmv_healthy)
gmv_cors
```

## Cortical Thickness
```{r}
thk_healthy <- thk_all %>% 
  filter(phys_ment_health == 0) %>% 
  filter(eventname == "baseline_year_1_arm_1")
thk_cors <- cor_mat_non_para(thk_healthy)
thk_cors
```


# Run Another Round of Correlations Using Spearman 
## GMV
```{r}
# Select the desired columns
smri_list <- gmv_healthy %>% 
  select(age, smri_vol_cdk_banksstslh:smri_vol_scs_subcorticalgv) %>%
  names()

# Calculate Kendall's tau correlations using corrr
kendall_tau_results <- corrr::correlate(gmv_healthy[, smri_list], method = "spearman")

# Extract Kendall's tau values for "column1"
kendall_tau_results %>% select(term, age) %>% mutate(age = abs(age)) %>% arrange(-age)


```

## Cortical Thickness
```{r}
# Select the desired columns
smri_list <- thk_healthy %>% 
  select(age, smri_thick_cdk_banksstslh:smri_thick_cdk_mean) %>%
  names()

# Calculate Kendall's tau correlations using corrr
kendall_tau_results <- corrr::correlate(thk_healthy[, smri_list], method = "spearman")

# Extract Kendall's tau values for "column1"
kendall_tau_results %>% select(term, age) %>% mutate(age = abs(age)) %>% arrange(-age)
```



# Select ROIs above the median correlation
## GMV
```{r}
# Using Median here
sub_rois_gmv <- as.data.frame(gmv_cors) %>% filter(gmv_cors < median(gmv_cors)) %>% select(-gmv_cors)
sub_rois_gmv <- tibble::rownames_to_column(sub_rois_gmv, "a") 
sub_rois_list_gmv <- sub_rois_gmv$a
sub_rois_list_gmv
gmv_sub <- gmv_all %>% select(-sub_rois_list_gmv)

```

# Cortical Thickness
```{r}
# Using Median here
sub_rois_thk <- as.data.frame(thk_cors) %>% filter(thk_cors < median(thk_cors)) %>% select(-thk_cors)
sub_rois_thk <- tibble::rownames_to_column(sub_rois_thk, "a") 
sub_rois_list_thk <- sub_rois_thk$a
sub_rois_list_thk
thk_sub <- thk_all %>% select(-sub_rois_list_thk)

```



# Check Distributions
## GMV
```{r}
smri_list <- colnames(gmv_sub %>% select(contains("smri")))

for (smri in 1:length(smri_list)) {
  hist(gmv_sub[, smri_list[smri]], xlab = smri_list[smri])
}
```

## Cortical Thickness
```{r}
smri_list <- colnames(thk_sub %>% select(contains("smri")))

for (smri in 1:length(smri_list)) {
  hist(thk_sub[, smri_list[smri]], xlab = smri_list[smri])
}
```


# Check Direction
## GMV
```{r}

smri_list <- colnames(gmv_sub %>% select(contains("smri")))
# Create a plot for each GMV
for (smri in smri_list) {
  p <- ggplot(gmv_sub %>% filter(eventname == "baseline_year_1_arm_1"), aes_string(x="age", y=smri)) +
    geom_point(aes(color = as.factor(sex))) +
    geom_smooth(method = "lm", aes(color = as.factor(sex)), se = FALSE) +
    labs(x="Age", y=smri, title=paste("Scatterplot of Age vs", smri)) +
    scale_color_manual(values = c("blue", "red"))
  print(p)
}

```
### Get correlations to see direction
```{r}

# Select the range of columns and chronological age column
selected_cols <- c(paste0("smri_vol_cdk_ifpllh:smri_vol_scs_subcorticalgv"), "age")

# Calculate correlation values
correlation_with_age <- gmv_sub %>%
  select(smri_vol_cdk_cuneuslh:smri_vol_scs_subcorticalgv, age) %>%
  summarise_all(~ cor(., gmv_sub$age))

# Print correlation values
cor_age_arrange <- arrange(as.data.frame(t(correlation_with_age)))

# Get names of negative and positive correlations
cor_age_arrange_neg <- cor_age_arrange %>% filter(V1 < 0.0) %>% rownames()
cor_age_arrange_pos <- cor_age_arrange %>% filter(V1 > 0.0) %>% rownames()

# Flip negative values to positive for the sake of brain age calcs.
gmv_sub_flip <- gmv_sub %>%
  mutate_at(vars(cor_age_arrange_neg), funs(max(.) - .))

smri_list <- colnames(gmv_sub_flip %>% select(contains("smri")))
# Create a plot for each GMV
for (smri in smri_list) {
  p <- ggplot(gmv_sub_flip %>% filter(eventname == "baseline_year_1_arm_1"), 
              aes_string(x="age", y=smri)) +
    geom_point(aes(color = as.factor(sex))) +
    geom_smooth(method = "lm", aes(color = as.factor(sex)), se = FALSE) +
    labs(x="Age", y=smri, title=paste("Scatterplot of Age vs", smri)) +
    scale_color_manual(values = c("blue", "red"))
  print(p)
}

```


# Cortical Thickness
```{r}
smri_list <- colnames(thk_sub %>% select(contains("smri")))

# Create a plot for each Cortical Thickness ROI
for (smri in smri_list) {
  p <- ggplot(thk_sub, aes_string(x="age", y=smri)) +
    geom_point(aes(color = as.factor(sex))) +
    geom_smooth(method = "lm", aes(color = as.factor(sex)), se = FALSE) +
    labs(x="Age", y=smri, title=paste("Scatterplot of Age vs", smri)) +
    scale_color_manual(values = c("blue", "red"))
  print(p)
}
```

### Get correlations to see direction
```{r}
colnames(thk_sub)
# Select the range of columns and chronological age column
selected_cols <- c(paste0("smri_thick_cdk_banksstslh:smri_thick_cdk_mean"), "age")
# Calculate correlation values
correlation_with_age <- thk_sub %>%
  select(smri_thick_cdk_banksstslh:smri_thick_cdk_mean, age) %>%
  summarise_all(~ cor(., thk_sub$age))

# Print correlation values
cor_age_arrange <- arrange(as.data.frame(t(correlation_with_age)))

# Get names of negative and positive correlations
cor_age_arrange_neg <- cor_age_arrange %>% filter(V1 < 0.0) %>% rownames()
cor_age_arrange_pos <- cor_age_arrange %>% filter(V1 > 0.0) %>% rownames()

# Flip negative values to positive for the sake of brain age calcs.
thk_sub_flip <- thk_sub %>%
  mutate_at(vars(cor_age_arrange_neg), funs(max(.) - .))

smri_list <- colnames(thk_sub_flip %>% select(contains("smri")))
# Create a plot for each GMV
for (smri in smri_list) {
  p <- ggplot(thk_sub_flip, aes_string(x="age", y=smri)) +
    geom_point(aes(color = as.factor(sex))) +
    geom_smooth(method = "lm", aes(color = as.factor(sex)), se = FALSE) +
    labs(x="Age", y=smri, title=paste("Scatterplot of Age vs", smri)) +
    scale_color_manual(values = c("blue", "red"))
  print(p)
}

```



# Check Outlier Participants and Filter out for healthy only
## GMV
```{r}
# I need to standardize first to see which participants need to be removed because they are
# outliers.

standardize <- function(df, start_string, end_string) {

  ## Males
  gmv_forScale_male <- df %>% filter(sex == 1)

  gmv_forScale_male <- gmv_forScale_male %>%
    mutate(across(starts_with(start_string):ends_with(end_string), scale))

  ## Females
  gmv_forScale_female <- df %>% filter(sex == 2)

  gmv_forScale_female <- gmv_forScale_female %>%
    mutate(across(starts_with(start_string):ends_with(end_string), scale))

  return(rbind(gmv_forScale_male, gmv_forScale_female))
}


# standardize on healthy baseline participants
gmv_sub_flip_stand_base_healthy <- standardize(gmv_sub_flip %>% 
                                    filter(eventname == "baseline_year_1_arm_1") %>%
                                    filter(phys_ment_health == 0), 
                                  "smri_vol_cdk_cuneuslh", 
                                  "smri_vol_scs_subcorticalgv")


gmv_sub_flip_stand_base_healthy_outlierRem <- gmv_sub_flip_stand_base_healthy %>%
  filter(phys_ment_health == 0) %>%
  rowwise() %>%
  mutate(outlier = any(abs(c_across(smri_vol_cdk_cuneuslh:smri_vol_scs_subcorticalgv)) > 2.5)) %>%
  ungroup() %>%
  filter(outlier == FALSE)


# Semi_join original non-standardized df with outliers removed standardized df
gmv_sub_flip_healthy_outlier_removed <- gmv_sub_flip %>% 
  filter(phys_ment_health == 0) %>%
  filter(eventname == "baseline_year_1_arm_1") %>%
  semi_join(gmv_sub_flip_stand_base_healthy_outlierRem, by = c("src_subject_id", "eventname"))


# Re-merge with unhealthy at baseline
gmv_sub_unhealthy_base <- gmv_sub_flip %>% 
  filter(phys_ment_health > 0) %>% 
  filter(eventname == "baseline_year_1_arm_1")

# All corrected baseline values
gmv_sub_base <- rbind(gmv_sub_unhealthy_base, gmv_sub_flip_healthy_outlier_removed)

# Merge with 2 and 4 year data
gmv_all_corrected <- rbind(gmv_sub_base, 
                           gmv_sub_flip %>% 
                             filter(eventname != "baseline_year_1_arm_1"))

```

## Cortical Thickness
```{r}
# 
# thk_sub_healthy <- thk_sub %>%
#   filter(phys_ment_health == 0) %>%
#   rowwise() %>%
#   mutate(outlier = any(abs(c_across(smri_thick_cdk_cuneuslh:smri_thick_cdk_mean)) > 3.5)) %>%
#   ungroup() %>%
#   filter(outlier == FALSE)
# 
# # Re-merge
# thk_sub_unhealthy <- thk_sub %>% filter(phys_ment_health > 0)
# 
# 
# thk_sub_all <- rbind(thk_sub_unhealthy, thk_sub_healthy %>% select(-outlier))
```

# Backward Selection
## GMV
```{r, echo=T, results='hide'}
# gmv_sub_healthy %>% select(-outlier)
# 
# # Perform backward selection
# model <- lm(age ~ ., data = gmv_sub_healthy %>% 
#               select(-outlier) %>% 
#               select(smri_vol_cdk_cuneuslh:smri_vol_scs_subcorticalgv, age))  # Initial model with selected GMV ROIs
# 
# while (length(coef(model)) > 1) {
#   pvals <- summary(model)$coefficients[, "Pr(>|t|)"][-1]
#   max_pval <- max(pvals)
#   
#   if (max_pval > 0.05) {
#     max_pval_index <- which(pvals == max_pval)
#     variable_to_remove <- names(pvals)[max_pval_index]
#     
#     # Update the model by removing the variable with the highest p-value
#     model <- update(model, paste(". ~ . - ", variable_to_remove))
#   } else {
#     break
#   }
# }
# 
# # Final selected GMV ROIs
# selected_gmv_rois <- names(coef(model))[-1]
# selected_gmv_rois

gmv_sub_flip_healthy_base <- gmv_all_corrected %>% 
  filter(phys_ment_health == 0) %>%
  filter(eventname == "baseline_year_1_arm_1")


# Backward Selection using step function with AIC
# Perform backward selection
model <- lm(age ~ ., data = gmv_sub_flip_healthy_base %>% 
              select(smri_vol_cdk_cuneuslh:smri_vol_scs_subcorticalgv, age))  # Initial model with selected GMV ROIs

# Perform backward stepwise selection using the 'step' function
selected_model <- step(model, direction = "both")

# Final selected GMV ROIs
selected_gmv_rois <- names(coef(selected_model))[-1]
selected_gmv_rois




```

## Cortical Thickness
```{r}

# Backward Selection using step function with AIC
# Perform backward selection
model <- lm(age ~ ., data = thk_sub_healthy %>% 
              select(-outlier) %>% 
              select(smri_thick_cdk_banksstslh:smri_thick_cdk_mean, age))  # Initial model with selected GMV ROIs

# Perform backward stepwise selection using the 'step' function
selected_model <- step(model, direction = "both")

# Final selected GMV ROIs
selected_thk_rois <- names(coef(selected_model))[-1]
selected_thk_rois


```

## GMV and Cortical Thickness
### Merge Dataframes
```{r}

gmv_thk_sub_healthy <- merge(gmv_sub_healthy %>% select(src_subject_id, eventname, 
                                 smri_vol_cdk_cuneuslh:smri_vol_scs_subcorticalgv, age),
      thk_sub_healthy %>% select(src_subject_id, eventname, 
                                 smri_thick_cdk_banksstslh:smri_thick_cdk_mean, age), 
      by = c("src_subject_id", "eventname"))

gmv_thk_sub_healthy <- gmv_thk_sub_healthy %>%
  mutate(age = coalesce(age.x, age.y)) %>%
  select(-age.x, -age.y)

gmv_thk_sub_all <- merge(gmv_sub_all, thk_sub_all, by = c("src_subject_id", "eventname"))


# Base names of columns to merge
columns_to_merge <- c("ment_health", "phys_health", "phys_ment_health", "demo_sex_v2", 
                      "site_id_l", "rel_family_id", "interview_age", "sex", "age")

# Function to merge .x and .y columns for a single column base name
merge_columns <- function(df, colname) {
  x_col <- paste0(colname, ".x")
  y_col <- paste0(colname, ".y")
  
  df <- df %>%
    mutate(!!colname := coalesce(!!sym(x_col), !!sym(y_col))) %>%
    select(-!!sym(x_col), -!!sym(y_col))
  
  return(df)
}

# Apply the function for each column base name
for (col in columns_to_merge) {
  gmv_thk_sub_all <- merge_columns(gmv_thk_sub_all, col)
}
```


### Run StepAIC
```{r, echo=T, results='hide'}

# Backward Selection using step function with AIC
# Perform backward selection
model <- lm(age ~ ., data = gmv_thk_sub_healthy %>% 
              select(smri_thick_cdk_banksstslh:smri_thick_cdk_mean,
                     smri_vol_cdk_cuneuslh:smri_vol_scs_subcorticalgv, age))  # Initial model with selected GMV ROIs

# Perform backward stepwise selection using the 'step' function
selected_model <- step(model, direction = "both")

# Final selected GMV ROIs
selected_gmv_thk_rois <- names(coef(selected_model))[-1]
selected_gmv_thk_rois


```


# Take out redundant areas and areas not selected by StepAIC
## GMV
```{r}
gmv_take_out <- setdiff(
  names(gmv_sub_all %>% 
          select(smri_vol_cdk_cuneuslh:smri_vol_scs_subcorticalgv)),
  selected_gmv_rois
)

gmv_sub_corrected_stepaic <- gmv_all_corrected %>% 
  select(-any_of(gmv_take_out))


```

## Cortical Thickness
```{r}

# GMV columns to take out from backward selection
thk_take_out <- setdiff(names(thk_sub_all %>% 
                                select(smri_thick_cdk_banksstslh:smri_thick_cdk_mean)), 
                        selected_thk_rois)

thk_take_out

thk_sub_base <- thk_sub_all %>% select(-c(thk_take_out, smri_thick_cdk_meanlh, smri_thick_cdk_meanrh, 
                                      smri_thick_cdk_mean, smri_thick_cdk_suplrh, smri_thick_cdk_supllh))

```

## Both
```{r}


# GMV columns to take out from backward selection
gmv_thk_take_out <- setdiff(names(gmv_thk_sub_all %>% 
                                select(smri_thick_cdk_banksstslh:smri_thick_cdk_mean,
                                       smri_vol_cdk_cuneuslh:smri_vol_scs_subcorticalgv)), 
                        selected_gmv_thk_rois)

gmv_thk_take_out

gmv_thk_sub_base <- gmv_thk_sub_all %>% select(-c(gmv_thk_take_out, smri_thick_cdk_meanlh, 
                                                  smri_thick_cdk_meanrh, smri_thick_cdk_mean, 
                                                  smri_thick_cdk_suplrh, smri_thick_cdk_supllh,
                                                  smri_vol_cdk_totallh, smri_vol_scs_subcorticalgv))

```


# Check Distribution again
## GMV Healthy
```{r}
smri_list <- colnames(gmv_sub_corrected_stepaic %>% select(contains("smri")))

for (smri in smri_list) {
  hist_data <- gmv_sub_corrected_stepaic %>%
    filter(phys_ment_health ==  1) %>%
    pull(smri) %>%
    as.numeric()

  hist(hist_data, main = paste("Histogram of", smri))
}

```

# Export 5.1 Outlier Removed, StepAIC selected GMVs, all time points
```{r}
gmv_sub_corrected_stepaic
gmv_sub_corrected_stepaic %>% filter(eventname == "baseline_year_1_arm_1") %>% 
  filter(phys_health_bin == 0) 
write.csv(gmv_sub_corrected_stepaic, paste0(root, "Version5.0_Exported_Data/gmv_sub_corrected_stepaic.csv"))
```



## Cortical Thickness
```{r}
smri_list <- colnames(thk_sub_base %>% select(contains("smri")))

for (smri in smri_list) {
  hist(thk_sub_base %>% filter(phys_ment_health == 0) %>% select(smri) %>% unlist() %>% as.numeric())
}

```

# Check ROIs with large variances


# Match 2 year and 4 year dataframes with Baseline
## GMV
```{r}
gmv_sub_2year <- gmv_2year %>% select(all_of(colnames(gmv_sub_base)))
gmv_sub_4year <- gmv_4year %>% select(all_of(colnames(gmv_sub_base)))
```

## Cortical Thickness
```{r}
thk_sub_2year <- thk_2year %>% select(all_of(colnames(thk_sub_base)))
thk_sub_4year <- thk_4year %>% select(all_of(colnames(thk_sub_base)))
```

## Both
```{r}
gmv_thk_2year <- merge(gmv_2year, thk_2year, by = c("src_subject_id", "eventname"))
gmv_thk_4year <- merge(gmv_4year, thk_4year, by = c("src_subject_id", "eventname"))

# Base names of columns to merge
columns_to_merge <- c("ment_health", "phys_health", "phys_ment_health", "demo_sex_v2", 
                      "site_id_l", "rel_family_id", "interview_age", "sex", "age", 
                      "mri_info_manufacturer")

# Function to merge .x and .y columns for a single column base name
merge_columns <- function(df, colname) {
  x_col <- paste0(colname, ".x")
  y_col <- paste0(colname, ".y")
  
  if (all(c(x_col, y_col) %in% colnames(df))) {
    df <- df %>%
      mutate(!!colname := coalesce(!!sym(x_col), !!sym(y_col))) %>%
      select(-!!sym(x_col), -!!sym(y_col))
  }
  
  return(df)
}

# Apply the function for each column base name
for (col in columns_to_merge) { 
  gmv_thk_sub_base <- merge_columns(gmv_thk_sub_base, col)
  gmv_thk_2year <- merge_columns(gmv_thk_2year, col)
  gmv_thk_4year <- merge_columns(gmv_thk_4year, col)
}

gmv_thk_sub_2year <- gmv_thk_2year %>% select(all_of(colnames(gmv_thk_sub_base)))
gmv_thk_sub_4year <- gmv_thk_4year %>% select(all_of(colnames(gmv_thk_sub_base)))

```


# Merge GMV and Cortical Thickness
```{r}

write.csv(gmv_thk_sub_base, paste0(root, "Version5.0_Exported_Data/gmv_thk_sub_base.csv"))
write.csv(gmv_thk_sub_2year, paste0(root, "Version5.0_Exported_Data/gmv_thk_sub_2year.csv"))
write.csv(gmv_thk_sub_4year, paste0(root, "Version5.0_Exported_Data/gmv_thk_sub_4year.csv"))
```

# Participants with all three timepoints
```{r}
gmv_sub_3timepoints <- rbind(gmv_sub_base, rbind(gmv_sub_2year, gmv_sub_4year)) %>%
  group_by(src_subject_id) %>%
  filter(n_distinct(eventname) == 3) %>%
  ungroup()

write.csv(gmv_sub_3timepoints, paste0(root, "Version5.0_Exported_Data/gmv_sub_3timepoints.csv"))
```



# Export
```{r}
gmv_sub_base %>% filter(eventname == "baseline_year_1_arm_1") %>% filter(phys_health_bin == 0)
write.csv(gmv_sub_base, paste0(root, "Version5.0_Exported_Data/gmv_sub_base.csv"))
write.csv(gmv_sub_2year, paste0(root, "Version5.0_Exported_Data/gmv_sub_2year.csv"))
write.csv(gmv_sub_4year, paste0(root, "Version5.0_Exported_Data/gmv_sub_4year.csv"))


write.csv(thk_sub_base, paste0(root, "Version5.0_Exported_Data/thk_sub_base.csv"))
write.csv(thk_sub_2year, paste0(root, "Version5.0_Exported_Data/thk_sub_2year.csv"))
write.csv(thk_sub_4year, paste0(root, "Version5.0_Exported_Data/thk_sub_4year.csv"))


```







