---
title: "HC_ABCD_V1"
output:
  html_document:
    toc: true
    theme: united
date: '2022-09-20'
---

Look at clinical markers overtime to predict chronological age using ridge regression. This will be 
called the biological age. Then, I will compute the difference between biological age and actual
chronological age. Is this biological age gap a predictor of substance use, alcohol use, or smoking? 

Potential Markers chosen from common biomarkers in literature:

abcd_ybd01 
This instrument summarizes whole blood analysis from two tubes for hemoglobin, A1C, CBC, total cholesterol, HDL cholesterol, and Ferritin.
From this, I want to use A1C (Glycated Hemoglobin), CBC, HDL cholesterol, possibly - lymphocytes

Ferritin justification
https://www.sciencedirect.com/science/article/pii/S2212267218304866?casa_token=df8tuwoOl1oAAAAA:7JHZqMqBCm73EaNXx6GxC5cs68USvmmW8xuUnsS_vU96b4eA1jr8_Q1_johhJCHONfSOh6Dv_Q

lymphocytes justification
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5191888/

abcd_hsss01
Pubertal hormone levels (estradiol, testosterone, and DHEA). 
DHEA effects unclear in literature

Pubertal changes - Potential biomarker?

Pace of Age:
B ~ b0 + b1(Age) + (1|abcd_site) + (1|abcd_site:rel_family_id) + (1|abcd_site:rel_family_id:SubjID)
B is the biomarker


C Age ~ b0 + b1(Biomarker1) ... +  (1  + slopes | abcd_site) + (1 + slopes | abcd_site:rel_family_id) 
For each individual:
Use betas to predict BA for each individual
Use BA to find correlations with drug use at baseline
Use BA to find likelihood of alcohol abuse at second timepoint.

lme4 there is predict function.
Check whether BA is correlated with CA
Correct for bias
Check how many site ideas and family ids. Create a table to visualize the nesting structure
When I run the log reg, use mixed effect, glmer. If not, take a random subject for each family 

TODO
1. Organize data by merging site df and family df. Then merge biomarkers by subjid
2. Standardize variables
3. regress on age to get betas for each biomarker
4. Predict BA using betas
5. Correlations and predictions with drug use. Same time point is correlation or regression to control for co-variates. For future time points
use regression. Alcohol is a yes/no outcome, so then use logistic regression. Control for alcohol abuse. Interaction between BA and gender or race
at two years

```{r}
### Libraries
# install.packages("dplyr")
# install.packages("lmerTest")
#install.packages("ggthemes")
# install.packages("flexplot")
# devtools::install_github("dustinfife/flexplot")
library(flexplot)
library(magrittr)
library(knitr)
library(dplyr)
library(lme4)
library(lmerTest)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(skimr)
```

# Family and Site ID data 
## 
```{r}
### Import data and set directory
setwd("/Users/hansoochang/Drexel/ABCD")
# FamilyId <- read.csv("/Users/hansoochang/Drexel/ABCD/data/acspsw03.csv")
# SiteId <- read.csv("/Users/hansoochang/Drexel/ABCD/data/abcd_lt01.csv")
demographic <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/abcd-general/abcd_y_lt.csv")
sex <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/gender-identity-sexual-health/gish_y_gi.csv")

demographic <- merge(demographic,
                            sex %>% select(src_subject_id, eventname, kbi_sex_assigned_at_birth),
                            by = c("src_subject_id", "eventname"))

# Specify the columns you want to fill NAs in
columns_to_fill <- c("rel_family_id", "rel_birth_id", "kbi_sex_assigned_at_birth")

demographic_filled <- demographic %>%
  group_by(src_subject_id) %>%
  mutate(across(all_of(columns_to_fill), ~ifelse(is.na(.), first(na.omit(.)), .))) %>%
  ungroup() %>%
  rename(sex = kbi_sex_assigned_at_birth) %>% # Rename the column
  mutate(sex = recode(sex, `1` = "M", `2` = "F")) # Recode values


```

# Blood Biomarkers 
## Version 4.0 (2-Year)
```{r}
### Blood ###
wba <- read.csv("/Users/hansoochang/Drexel/ABCD/data/abcd_ybd01.csv")
table(wba$eventname)

# 979 participants with Hemoglobin A1C data. 
# wba[which(wba$biospec_blood_hemoglobin_a1 != ""),] 

# 716 participants with white blood count data.
# wba[which(wba$biospec_blood_wbc_count != ""),] 

# 1022 participants with Total Cholesterol data.
# wba[which(wba$biospec_blood_cholesterol != ""),] 

# 1022 participants with HDL Cholesterol data.
# wba[which(wba$biospec_blood_hdl_cholesterol != ""),] 

# 1023 participants with Ferritin data.
# wba[which(wba$biospec_blood_ferritin != ""),] 

# Remove first row because duplicate
wba1 <- wba[-1,]
row.names(wba1) <- NULL
colnames(wba1)
# Filter dataframe to have only biomarkers above
blood <- wba1[, c("interview_age","collection_id", "abcd_ybd01_id", "subjectkey", "src_subject_id",
                  "eventname", "biospec_blood_hemoglobin_a1", "biospec_blood_wbc_count",
                  "biospec_blood_cholesterol", "biospec_blood_hdl_cholesterol", 
                  "biospec_blood_ferritin" , "biospec_blood_baso_percent", "biospec_blood_baso_abs",
                  "biospec_blood_eos_percent", "biospec_blood_eos_abs", "biospec_blood_hemoglobin",
                  "biospec_blood_mcv", "biospec_blood_plt_count", "biospec_blood_imm_gran_per",
                  "biospec_blood_imm_gran_abs", "biospec_blood_lymph_percent", 
                  "biospec_blood_lymph_abs", "biospec_blood_mono_percent", "biospec_blood_mono_abs",
                  "biospec_blood_mpv", "biospec_blood_neut_percent", "biospec_blood_neut_abs",
                  "biospec_blood_rdw", "biospec_blood_rbc_count")]
# Took out neut_abs, hemotocrit because correlation of greater than 0.7

# Turn all no-value cells into NA
blood <- blood %>% mutate_all(na_if,"")

# Select rows with no NA's. A total of 687 participants 
blood_biomarkers <- blood[complete.cases(blood), ]

length(unique(wba[,"subjectkey"]))

```

## Version 5.0 (Up to 4 year)
```{r}
wba_5 <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.0/core/physical-health/ph_y_bld.csv", fill = NA)
table(wba_5$eventname)

bm <- c("biospec_blood_hemoglobin_a1", "biospec_blood_wbc_count", "biospec_blood_cholesterol",
        "biospec_blood_hdl_cholesterol", "biospec_blood_ferritin", "MAP", "BMI", "anthro_waist_cm",
         "biospec_blood_baso_abs",
                   "biospec_blood_eos_abs", "biospec_blood_hemoglobin",
                  "biospec_blood_mcv", "biospec_blood_plt_count",
                  "biospec_blood_imm_gran_abs",  
                  "biospec_blood_lymph_abs", "biospec_blood_mono_abs",
                  "biospec_blood_mpv",  "biospec_blood_neut_abs", 
                  "biospec_blood_rdw", "biospec_blood_rbc_count", "biospec_blood_hematocrit", "NLR",
        "LMR", "PLR")

wba_5_bms <- wba_5[, c("src_subject_id",
                  "eventname", "biospec_blood_hemoglobin_a1", "biospec_blood_wbc_count",
                  "biospec_blood_cholesterol", "biospec_blood_hdl_cholesterol", 
                  "biospec_blood_ferritin" , "biospec_blood_baso_percent", "biospec_blood_baso_abs",
                  "biospec_blood_eos_percent", "biospec_blood_eos_abs", "biospec_blood_hemoglobin",
                  "biospec_blood_mcv", "biospec_blood_plt_count", "biospec_blood_imm_gran_per",
                  "biospec_blood_imm_gran_abs", "biospec_blood_lymph_percent", 
                  "biospec_blood_lymph_abs", "biospec_blood_mono_percent", "biospec_blood_mono_abs",
                  "biospec_blood_mpv", "biospec_blood_neut_percent", "biospec_blood_neut_abs",
                  "biospec_blood_rdw", "biospec_blood_rbc_count")]

  
wba_5_bms[complete.cases(wba_5_bms$biospec_blood_rdw), ] %>% filter(eventname == "4_year_follow_up_y_arm_1")

hist(scale(wba_5_bms$biospec_blood_imm_gran_abs))
hist(scale(wba_5_bms$biospec_blood_imm_gran_per))

hist((wba_5_bms$biospec_blood_rdw))
```
Least amount of data available for given biomarker: 236 participants with information across at year 4.


# Blood Pressure.
According to Belsky (2015), Mean Arterial Pressure (MAP) was used to calculate blood pressure. 
Diastolic	Pressure+1/3(Systolic	Pressure - Diastolic	Pressure). The mean value for the three 
BP readings are used in this dataset

## Version 4.0
```{r}
### Blood Pressure ###
bp <- read.csv("/Users/hansoochang/Drexel/ABCD/data/abcd_bp01.csv")
table(bp$study_cohort_name)
# Drop first row because duplicate
bp <- bp[-1,]
row.names(bp) <- NULL

# Turn all no-value cells into NA
bp <- bp %>% mutate_all(na_if,"")

# Only rows with mean diastolic and mean systolic
bp1 <- bp[!is.na(bp$blood_pressure_dia_mean) | !is.na(bp$blood_pressure_sys_mean), ]

# Change datatype to numeric. Originally chr
bp1$blood_pressure_sys_mean <- as.numeric(as.character(bp1$blood_pressure_sys_mean))
bp1$blood_pressure_dia_mean <- as.numeric(as.character(bp1$blood_pressure_dia_mean))

bp1$MAP <- bp1$blood_pressure_dia_mean + (1/3)*(bp1$blood_pressure_sys_mean - 
                                               bp1$blood_pressure_dia_mean)

# Final blood pressure dataframe
bp_biomarker <- bp1[, c("subjectkey", "MAP")]
table(bp1$eventname)
```

## Version 5.0
```{r}
bp_5 <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.0/core/physical-health/ph_y_bp.csv", fill = NA)

table(bp_5$eventname)

bp_5 %>% 
  group_by(eventname) %>%
  skim()

# Only rows with mean diastolic and mean systolic
bp_51 <- bp_5[!is.na(bp_5$blood_pressure_dia_mean) | !is.na(bp_5$blood_pressure_sys_mean), ]

# Change datatype to numeric. Originally chr
bp_51$blood_pressure_sys_mean <- as.numeric(as.character(bp_51$blood_pressure_sys_mean))
bp_51$blood_pressure_dia_mean <- as.numeric(as.character(bp_51$blood_pressure_dia_mean))

bp_51$MAP <- bp_51$blood_pressure_dia_mean + (1/3)*(bp_51$blood_pressure_sys_mean - 
                                               bp_51$blood_pressure_dia_mean)


# Final blood pressure dataframe
bp_5_biomarker <- bp_51[, c("src_subject_id", "eventname", "MAP")]
```


# BMI and waist
https://downloads.hindawi.com/journals/bmri/2022/2146596.pdf

## Version 4.0
```{r}
hww <- read.csv("/Users/hansoochang/Drexel/ABCD/data/abcd_ant01.csv")

# Drop first row because duplicate. However, this removes the values of the average weight column
# because there is function that calculates the average weight in that first row.
hww <- hww[-1,]
row.names(hww) <- NULL

# Turn all no-value cells into NA
hww <- hww %>% mutate_all(na_if,"")

# Select only 2 year cohort
hww1 <- hww[which(hww$eventname == "2_year_follow_up_y_arm_1"), ]

# Change datatype to numeric. Originally chr
hww1$anthroweight1lb <- as.numeric(hww1$anthroweight1lb) 
hww1$anthroweight2lb <- as.numeric(hww1$anthroweight2lb) 
hww1$anthroweight3lb <- as.numeric(hww1$anthroweight3lb) 

# re-calculate means of weight
hww1$anthroweightcalc <- rowMeans(hww1[, c("anthroweight1lb", "anthroweight2lb", "anthroweight3lb")],
                                 na.rm=TRUE)

# Convert to kg
hww1$anthroweightcalc_kg <- hww1$anthroweightcalc*0.453592

# Change height datatype to numeric
hww1$anthroheightcalc <- as.numeric(hww1$anthroheightcalc) 

# Convert average height to meters
hww1$anthroheightcalc_m <- hww1$anthroheightcalc*0.0254

# Calculate BMI ratio. BMI = kg/(m^2)
hww1$BMI <- hww1$anthroweightcalc_kg/(hww1$anthroheightcalc_m^2)

# Final anthropomorphic dataframe
hww_biomarker <- hww1[, c("subjectkey", "BMI")]

# Use only complete rows
hww_biomarker <- hww_biomarker[complete.cases(hww_biomarker), ]

# 7.520 participants at 2-year mark.
head(hww_biomarker)

### For Ana ###
# hww_biomarker$src_subject_id <- hww_biomarker$subjectkey
# bmi_sex <- merge(hww_biomarker %>% select(src_subject_id, BMI), 
#       demographic_filled %>% 
#         select(src_subject_id, sex), 
#       by = c("src_subject_id"))
# 
# demographic_filled %>% filter(src_subject_id == "NDAR_INV107UCJ69")
# 
# bmi_sex <- bmi_sex %>%
#   group_by(src_subject_id) %>%
#   slice_max(order_by = BMI, with_ties = FALSE) %>%
#   ungroup()
# 
# bmi_sex_filtered <- bmi_sex %>% filter(!is.na(sex)) %>%
#   group_by(sex) %>%
#   filter(BMI > mean(BMI) - 4 * sd(BMI) & BMI < mean(BMI) + 4 * sd(BMI)) %>%
#   ungroup()
# 
# hist(bmi_sex_filtered$BMI)
# 
# write.csv(bmi_sex_filtered, "/Users/hansoochang/Drexel/ABCD/Version5.0_Exported_Data/bmi_sex_filtered.csv")

```

## Version 5.0
```{r}
hww_5 <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.0/core/physical-health/ph_y_anthro.csv")


# Change datatype to numeric. Originally chr
hww_5$anthroweight1lb <- as.numeric(hww_5$anthroweight1lb) 
hww_5$anthroweight2lb <- as.numeric(hww_5$anthroweight2lb) 
hww_5$anthroweight3lb <- as.numeric(hww_5$anthroweight3lb) 

# re-calculate means of weight
hww_5$anthroweightcalc <- rowMeans(hww_5[, c("anthroweight1lb", "anthroweight2lb", "anthroweight3lb")],
                                 na.rm=TRUE)

# Convert to kg
hww_5$anthroweightcalc_kg <- hww_5$anthroweightcalc*0.453592

# Change height datatype to numeric
hww_5$anthroheightcalc <- as.numeric(hww_5$anthroheightcalc) 

# Convert average height to meters
hww_5$anthroheightcalc_m <- hww_5$anthroheightcalc*0.0254

# Calculate BMI ratio. BMI = kg/(m^2)
hww_5$BMI <- hww_5$anthroweightcalc_kg/(hww_5$anthroheightcalc_m^2)

# Final anthropomorphic dataframe
hww_5_biomarker <- hww_5[, c("src_subject_id", "eventname","BMI")]

# 7.520 participants at 2-year mark.
head(hww_5_biomarker)

```



Physical Activity
https://downloads.hindawi.com/journals/bmri/2022/2146596.pdf
Average METs. MET minutes were used to index total physical activity. A MET is a metabolic
equivalent, the amount of energy expended at rest. Casual walking
produces about three METs, triple the energy expenditure
compared to sitting. If a person engaged in casual walking
for 30 minutes, then, MET minutes would be 90 (3 METs
× 30 minutes)

1 MET=Resting Metabolism of average individual (adult)= 3.5 ml/kg/min of O2 consumption
```{r}
pa <- read.csv("/Users/hansoochang/Drexel/ABCD/data/abcd_fbdpas01.csv")

# Drop first row because duplicate
pa <- pa[-1,]
row.names(pa) <- NULL

# Turn all no-value cells into NA
pa <- pa %>% mutate_all(na_if,"")

# only at 2 year follow up
pa1 <- pa[which(pa$eventname == "2_year_follow_up_y_arm_1"),]

# Convert to numeric
pa1$fit_ss_dayt_ave_met_value <- as.numeric(pa1$fit_ss_dayt_ave_met_value) 

# group by participant and get the average of the weekly MET averages.  
pa1_group <- pa1 %>% group_by(subjectkey) %>% summarise(MET_average = 
                                                         mean(fit_ss_dayt_ave_met_value))

# No NaN's
pa_biomarker <- pa1_group[complete.cases(pa1_group), ]

# 7,394 participants
pa_biomarker
```
I think I don't need this one above...

# Merging
## Version 4.0
```{r}
# ### Merge ###
# a <- merge(ID, blood_biomarkers, by = "subjectkey")
# b <- merge(a, bp_biomarker, by = "subjectkey")
# c <- merge(b, hww_biomarker, by = "subjectkey")
# 
# 
# # drop some unnecessary columns
# all_merge_drop <- c[, !colnames(c) %in% c("collection_id.x", "acspsw03_id",
#                                                           "dataset_id", "src_subject_id.x", 
#                                                           "eventname.x", "collection_id.y",
#                                                           "src_subject_id.y", "abcd_ybd01_id",
#                                                           "interview_age.x")]
# 
# # 658 total subjects
# final_merge <- all_merge_drop[complete.cases(all_merge_drop), ]
# nrow(final_merge)

```

## Version 5.0
```{r}
### Merge ###
a <- merge(demographic_filled %>% select(src_subject_id:rel_family_id, sex, interview_age), 
           wba_5_bms, by = c("src_subject_id", "eventname"))
b <- merge(a, bp_5_biomarker, by = c("src_subject_id", "eventname"))
table(b$eventname)
c <- merge(b, hww_5_biomarker, by = c("src_subject_id", "eventname"))
table(c$eventname)

c %>%
  group_by(src_subject_id) %>%  # Group data by participant ID
  filter(n_distinct(eventname) >= 2) %>%  # Keep only groups with at least 2 unique eventnames
  ungroup()  # Remove the grouping

final_merge <- c
```

## Participant numbers
```{r}
# complete cases
table(final_merge$eventname)

final_merge %>%
  group_by(src_subject_id) %>%
  summarize(num_years = n_distinct(eventname))%>%
  filter(num_years == 2) 

```
No one has all three years. The measures were only taken at 2 year and 4 year. Not sure where 3 year came from.



# Standardization
Standardization should be separate for men and women. HDL cholesterol declines with age, so this 
should be reversed. Previous literature has shown that physical activity also declines with age,
but this may not be true for children and teenagers.
```{r}
# ### Standardize ###
# 
# final_merge[,8:ncol(final_merge)] <- sapply(final_merge[,8:ncol(final_merge)], as.numeric)
# 
# # Make Ratio BMs
# # Neutrophil to Lymphocyte Ratio (NLR)
# # Lymphocyte to monocyte ratio (LMR)
# # Platelet to Lymphocyte Ratio (PLR)
# final_merge$NLR <- final_merge$biospec_blood_neut_abs / final_merge$biospec_blood_lymph_abs
# final_merge$LMR <- final_merge$biospec_blood_lymph_abs / final_merge$biospec_blood_mono_abs
# final_merge$PLR <- final_merge$biospec_blood_plt_count / final_merge$biospec_blood_lymph_abs
# 
# # List of Biomarkers
# bm <- c("biospec_blood_hemoglobin_a1", "biospec_blood_wbc_count", "biospec_blood_cholesterol",
#         "biospec_blood_hdl_cholesterol", "biospec_blood_ferritin", "MAP", "BMI",
#         "biospec_blood_baso_percent", "biospec_blood_baso_abs",
#                   "biospec_blood_eos_percent", "biospec_blood_eos_abs", "biospec_blood_hemoglobin",
#                   "biospec_blood_mcv", "biospec_blood_plt_count", "biospec_blood_imm_gran_per",
#                   "biospec_blood_imm_gran_abs", "biospec_blood_lymph_percent", 
#                   "biospec_blood_lymph_abs", "biospec_blood_mono_percent", "biospec_blood_mono_abs",
#                   "biospec_blood_mpv", "biospec_blood_neut_percent", "biospec_blood_neut_abs",
#                   "biospec_blood_rdw", "biospec_blood_rbc_count", "NLR",
#         "LMR", "PLR")
# 
# # Convert biomarkers to numeric
# 
# final_merge[bm] <- sapply(final_merge[bm], as.numeric)
# 
# 
# # Reverse BMs which are negatively associated with higher BA
# # High NLR, high PLR, low LMR at baseline are significantly associated with
# # poor overall survival - Chan, 2017
# final_merge[, "biospec_blood_hdl_cholesterol"] <- -1*(final_merge[, "biospec_blood_hdl_cholesterol"])
# final_merge[, "LMR"] <- -1*(final_merge[, "LMR"])
# 
# View(final_merge)
# 
# write.csv(final_merge, "/Users/hansoochang/Drexel/ABCD/data/bm_unstand.csv")
# 
# skim(final_merge[, c("NLR", "LMR", "PLR")])
```


```{r}
# ## Men (361) ##
# men_merge <- final_merge[which(final_merge$sex == "M"),]
# nrow(men_merge)
# 
# # scale biomarkers
# men_merge[, bm] <- as.data.frame(scale(men_merge[,bm]))
# 
# 
# ## Women (296) ##
# women_merge <- final_merge[which(final_merge$sex == "F"),]
# nrow(women_merge)
# 
# # scale biomarkers
# women_merge[, bm] <- as.data.frame(scale(women_merge[,bm]))
# 
# 
# ## Remerge men and women ##
# stand <- rbind(men_merge, women_merge)
# 
# head(stand)
# 
# write.csv(stand, "/Users/hansoochang/Drexel/ABCD/data/biomarkers.csv")
```


# Standardization 5.0
I shouldn't standardize... it skews later timepoints.
```{r}
### Standardize ###
final_merge <- final_merge %>% mutate_at(vars(biospec_blood_hemoglobin_a1:BMI), as.numeric)
# Make Ratio BMs
# Neutrophil to Lymphocyte Ratio (NLR)
# Lymphocyte to monocyte ratio (LMR)
# Platelet to Lymphocyte Ratio (PLR)
final_merge$NLR <- final_merge$biospec_blood_neut_abs / final_merge$biospec_blood_lymph_abs
final_merge$LMR <- final_merge$biospec_blood_lymph_abs / final_merge$biospec_blood_mono_abs
final_merge$PLR <- final_merge$biospec_blood_plt_count / final_merge$biospec_blood_lymph_abs

# List of Biomarkers
bm <- c("biospec_blood_hemoglobin_a1", "biospec_blood_wbc_count", "biospec_blood_cholesterol",
        "biospec_blood_hdl_cholesterol", "biospec_blood_ferritin", "MAP", "BMI",
        "biospec_blood_baso_percent", "biospec_blood_baso_abs",
                  "biospec_blood_eos_percent", "biospec_blood_eos_abs", "biospec_blood_hemoglobin",
                  "biospec_blood_mcv", "biospec_blood_plt_count", "biospec_blood_imm_gran_per",
                  "biospec_blood_imm_gran_abs", "biospec_blood_lymph_percent", 
                  "biospec_blood_lymph_abs", "biospec_blood_mono_percent", "biospec_blood_mono_abs",
                  "biospec_blood_mpv", "biospec_blood_neut_percent", "biospec_blood_neut_abs",
                  "biospec_blood_rdw", "biospec_blood_rbc_count", "NLR",
        "LMR", "PLR")

# Convert biomarkers to numeric
final_merge_num <- final_merge %>% mutate_at(vars(biospec_blood_hemoglobin_a1:PLR), as.numeric)
```

```{r}
# Reverse BMs which are negatively associated with higher BA
# High NLR, high PLR, low LMR at baseline are significantly associated with
# poor overall survival - Chan, 2017
# final_merge_num[, "biospec_blood_hdl_cholesterol"] <- -1*(final_merge_num[, "biospec_blood_hdl_cholesterol"])
# final_merge_num[, "LMR"] <- -1*(final_merge_num[, "LMR"])
# final_merge_num
# ## Men (655) ##
# men_merge <- final_merge_num[which(final_merge$sex == "M"),]
# nrow(men_merge)
# 
# # scale biomarkers
# men_merge[, bm] <- as.data.frame(scale(men_merge[,bm]))
# 
# ## Women (526) ##
# women_merge <- final_merge[which(final_merge$sex == "F"),]
# nrow(women_merge)
# 
# # scale biomarkers
# women_merge[, bm] <- as.data.frame(scale(women_merge[,bm]))
# 
# 
# ## Remerge men and women ##
# stand_5 <- rbind(men_merge, women_merge)

# Just write the final_merge_num as the final biomarkers_5 csv file
write.csv(final_merge_num, "/Users/hansoochang/Drexel/ABCD/Version5.0_Exported_Data/biomarkers_5.csv")


### For Ana ###
```


Modelling

Determining Random Effects Structures
```{r}
length(unique(stand$subjectkey)) # 659
length(unique(stand$rel_family_id))# 599
length(unique(stand$site_id_l)) # 21
```

```{r}
library(corrplot)

corr <- cor(stand[bm])
corrtab <- as.data.frame(as.table(corr))
corrtab[order(corrtab$Freq), ]


```
We can see here that there is some multicollinearity issues, which is not a surprise. Let's take out
BM's with percentages since these are redundant.

```{r}
bm <- c("biospec_blood_hemoglobin_a1", "biospec_blood_wbc_count", "biospec_blood_cholesterol",
        "biospec_blood_hdl_cholesterol", "biospec_blood_ferritin", "MAP", "BMI", "anthro_waist_cm",
         "biospec_blood_baso_abs",
                   "biospec_blood_eos_abs", "biospec_blood_hemoglobin",
                  "biospec_blood_mcv", "biospec_blood_plt_count",
                  "biospec_blood_imm_gran_abs",  
                  "biospec_blood_lymph_abs", "biospec_blood_mono_abs",
                  "biospec_blood_mpv",  "biospec_blood_neut_abs", 
                  "biospec_blood_rdw", "biospec_blood_rbc_count", "biospec_blood_hematocrit", "NLR",
        "LMR", "PLR")


corr <- cor(stand[bm])
corrtab <- as.data.frame(as.table(corr))
corrtab[order(corrtab$Freq), ]

```
All correlations are below 0.7 now.



It's better not to use family ID as a random effect structure because it seems like there aren't 
that many siblings. 

Maybe gender could also be a random effects structure?

C Age ~ b0 + b1(Biomarker1) ... +  (1  + slopes | abcd_site)
For each individual:
Use betas to predict BA for each individual
Use BA to find correlations with drug use at baseline
Use BA to find likelihood of alcohol abuse at second timepoint.
```{r}
library("modelsummary")

attach(stand)

### No random effects
base <- lm(as.numeric(interview_age.y) ~ biospec_blood_hemoglobin_a1 + biospec_blood_wbc_count + 
               biospec_blood_cholesterol + biospec_blood_hdl_cholesterol + biospec_blood_ferritin +
               MAP + BMI + biospec_blood_baso_abs+
                  biospec_blood_eos_abs+ biospec_blood_hemoglobin+
                   biospec_blood_mcv+ biospec_blood_plt_count+
                   biospec_blood_imm_gran_abs+ 
                  biospec_blood_lymph_abs + biospec_blood_mono_abs+
                   biospec_blood_mpv+ 
                   biospec_blood_rdw+ biospec_blood_rbc_count+  NLR+
         LMR+ PLR, data = stand)

### Random slopes included for site_id and family_id Maximal
### DOES NOT CONVERGE
mod1 <- lmer(as.numeric(interview_age.y) ~ biospec_blood_hemoglobin_a1 + biospec_blood_wbc_count + 
               biospec_blood_cholesterol + biospec_blood_hdl_cholesterol + biospec_blood_ferritin +
               MAP + BMI + biospec_blood_baso_abs+
                  biospec_blood_eos_abs+ biospec_blood_hemoglobin+
                   biospec_blood_mcv+ biospec_blood_plt_count+
                   biospec_blood_imm_gran_abs+ 
                  biospec_blood_lymph_abs + biospec_blood_mono_abs+
                   biospec_blood_mpv+ 
                   biospec_blood_rdw+ biospec_blood_rbc_count+  NLR+
         LMR+ PLR + 
               (1 + biospec_blood_hemoglobin_a1 + biospec_blood_wbc_count + 
               biospec_blood_cholesterol + biospec_blood_hdl_cholesterol + biospec_blood_ferritin +
               MAP + BMI + biospec_blood_baso_abs+
                  biospec_blood_eos_abs+ biospec_blood_hemoglobin+
                   biospec_blood_mcv+ biospec_blood_plt_count+
                   biospec_blood_imm_gran_abs+ 
                  biospec_blood_lymph_abs + biospec_blood_mono_abs+
                   biospec_blood_mpv+ 
                   biospec_blood_rdw+ biospec_blood_rbc_count+  NLR+
         LMR+ PLR | site_id_l), data = stand, # (slopes | rel_family_id)
                 control = lmerControl(optimizer = "bobyqa"), REML = F) 
# Takes too long

### Random slopes included for site_id and family_id Maximal
mod1_plus <- lmer(as.numeric(interview_age.y) ~ biospec_blood_hemoglobin_a1 + biospec_blood_wbc_count + 
               biospec_blood_cholesterol + biospec_blood_hdl_cholesterol + biospec_blood_ferritin +
               MAP + BMI + biospec_blood_baso_abs+
                  biospec_blood_eos_abs+ biospec_blood_hemoglobin+
                   biospec_blood_mcv+ biospec_blood_plt_count+
                   biospec_blood_imm_gran_abs+ 
                  biospec_blood_lymph_abs + biospec_blood_mono_abs+
                   biospec_blood_mpv+ 
                   biospec_blood_rdw+ biospec_blood_rbc_count+  NLR+
         LMR+ PLR +  
               (1 | site_id_l) + (1 | rel_family_id), data = stand, # (slopes | rel_family_id)
                 control = lmerControl(optimizer = "bobyqa"), REML = F)

# Run model anovas for each random effect slope added in. 

### No random slopes for site_id
mod2 <- lmer(as.numeric(interview_age.y) ~ biospec_blood_hemoglobin_a1 + biospec_blood_wbc_count + 
               biospec_blood_cholesterol + biospec_blood_hdl_cholesterol + biospec_blood_ferritin +
               MAP + BMI + biospec_blood_baso_abs+
                  biospec_blood_eos_abs+ biospec_blood_hemoglobin+
                   biospec_blood_mcv+ biospec_blood_plt_count+
                   biospec_blood_imm_gran_abs+ 
                  biospec_blood_lymph_abs + biospec_blood_mono_abs+
                   biospec_blood_mpv+ 
                   biospec_blood_rdw+ biospec_blood_rbc_count+  NLR+
         LMR+ PLR + 
               (1 | site_id_l), data = stand, 
                 control = lmerControl(optimizer = "bobyqa"), REML = F)
# Clustering by site
mod3 <- lmer(as.numeric(interview_age.y) ~ (1 | site_id_l), data = stand, 
             control = lmerControl(optimizer = "bobyqa"), REML = F)



coef(summary(base))
coef(summary(mod1))
coef(summary(mod2))

get_gof(base)
get_gof(mod1)
get_gof(mod2)



```
My sample size was not large enough to support the maximal random effects structure. However,
the difference between the first and second models show that the location of data collection has an
arguable significant effect on the biomarkers predicting age. I could not add any random slopes to 
family id, most likely because there are too many different families or in other words, not enough 
siblings in the sample.

The second model performed slightly better than the first considering the rmse. However, this may be 
biased as it does not take into account individual differences. Both models are most likely biased 
as well, which will need to be corrected later.

More Model Comparison
```{r}
icc(mod1)
icc(mod2)
icc(mod3) # 5% of variance in chronological age due to site.

model.comparison(mod1, mod2)
```


```{r, results='hide'}
summary(mod2)
ranef(mod2)
```


Extracting Betas and Correlation with Chronological age
```{r}
library("Metrics")
library("irr")

# These fitted values are the predictions of age that our model made. This is our "biological age"
BA <- predict(mod1_plus)
write.csv(BA, "/Users/hansoochang/Drexel/ABCD/data/BA")

co_df <- cbind(as.data.frame(BA), as.data.frame(stand$interview_age.y))
View(co_df)

co_df$`stand$interview_age.y` <- as.numeric(co_df$`stand$interview_age.y`)


# Correlation, rmse, mae of BA and CA
cor.test(co_df$BA, as.numeric(stand$interview_age.y))
rmse(co_df$BA, as.numeric(stand$interview_age.y))
mae(co_df$BA, as.numeric(stand$interview_age.y))
icc(co_df, model = "twoway", type = "agreement", unit =
      "single")

```
Adding rel_family_id as a random effect structure drastically improves correlation
Convert to years 


# Population characteristics
```{r}
stand

# Find same family
fam <- as.data.frame(table(stand$rel_family_id))
fam[fam$Freq > 1, ] # 57 duplictes, meaning 114 participants with sibling in study

# site
table(stand$site_id_l)

# eventname
table(stand$eventname.y)

```





# 4 Year Follow Up (VER 5.0)
```{r}
wba_5 <- read.csv("/Users/hansoochang/Downloads/abcd-data-release-5.0/core/physical-health/ph_y_bld.csv", fill = NA)
head(wba_5)

```

  

