---
title: "KDM_BrainAge_Projections_5.0"
output: html_document
date: "2023-07-20"
---

This file projects the trained KDM baseline data to year 2 and year 4 for all brain ages.


Input:
+ kdm_data_gmv_sub.csv (Projected Baseline KDM)
+ kdm_train_gmv_sub (Trained Model Fit)

Output:
+ 


# Libraries
```{r}
library(BioAge)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(stats)
library(skimr)
library(pcaPP)
library(stringr)
library(stats)
library(misty)
library(emmeans)
```


# Read in files
```{r}
kdm_train_gmv_sub <- readRDS(paste0(root, "/summary_data/kdm_train_gmv_sub.rds"))

kdm_data_gmv_sub_base <- read.csv(paste0(root, 
                                         "Version5.0_Exported_Data/kdm_data_gmv_sub_baseline.csv")) %>%
  select(-starts_with("X"))


gmv_sub_2year <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_sub_all_stepaic.csv")) %>%
  filter(eventname == "2_year_follow_up_y_arm_1") %>%
  select(-starts_with("X"))

gmv_sub_4year <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_sub_all_stepaic.csv")) %>%
  filter(eventname == "4_year_follow_up_y_arm_1") %>%
  select(-starts_with("X"))

# gmv_sub_2year <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_sub_2year.csv"))
# gmv_sub_4year <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_sub_4year.csv"))

brain_markers_sub <- colnames(gmv_sub_2year %>% select(contains("smri")))

colnames(kdm_data_gmv_sub_base)
colnames(gmv_sub_2year)
```

# Project to 2 Year
```{r}
kdm_gmv_sub_2year <- kdm_calc(gmv_sub_2year, biomarkers = brain_markers_sub, fit = kdm_train_gmv_sub$fit, s_ba2 = 
                       kdm_train_gmv_sub$fit$s_ba2)

kdm_data_gmv_sub_2year <- kdm_gmv_sub_2year$data


```

# 2 Year Metrics
```{r}
nrow(kdm_data_gmv_sub_2year)
cor.test(as.numeric(kdm_data_gmv_sub_2year$kdm), as.numeric(kdm_data_gmv_sub_2year$age))
Metrics::rmse(as.numeric(kdm_data_gmv_sub_2year$kdm), as.numeric(kdm_data_gmv_sub_2year$age))
Metrics::mae(as.numeric(kdm_data_gmv_sub_2year$kdm), as.numeric(kdm_data_gmv_sub_2year$age))

kdm_data_gmv_sub_2year$gender <- as.factor(kdm_data_gmv_sub_2year$sex)
plot_ba(kdm_data_gmv_sub_2year, "kdm", "KDM\nBiological Age")

```


# Project to 4 Year
```{r}
kdm_gmv_sub_4year <- kdm_calc(gmv_sub_4year, biomarkers = brain_markers_sub, fit = kdm_train_gmv_sub$fit, s_ba2 = 
                       kdm_train_gmv_sub$fit$s_ba2)

kdm_data_gmv_sub_4year <- kdm_gmv_sub_4year$data
```


# 4 Year Metrics
```{r}
nrow(kdm_data_gmv_sub_4year)
cor.test(as.numeric(kdm_data_gmv_sub_4year$kdm), as.numeric(kdm_data_gmv_sub_4year$age))
Metrics::rmse(as.numeric(kdm_data_gmv_sub_4year$kdm), as.numeric(kdm_data_gmv_sub_4year$age))
Metrics::mae(as.numeric(kdm_data_gmv_sub_4year$kdm), as.numeric(kdm_data_gmv_sub_4year$age))


kdm_data_gmv_sub_4year$gender <- as.factor(kdm_data_gmv_sub_4year$sex)
plot_ba(kdm_data_gmv_sub_4year, "kdm", "KDM\nBiological Age")
```


# Participants with all 3 Timepoints (Long)
```{r}
bind1 <- rbind(kdm_data_gmv_sub_base %>% 
                 select(src_subject_id, eventname, phys_ment_health:gender, mri_info_manufacturer) %>%
                 select(-phys_ment_health_bin), 
                kdm_data_gmv_sub_2year %>% 
                 select(src_subject_id, eventname, phys_ment_health:gender, mri_info_manufacturer))


kdm_data_gmv_sub_long <- rbind(bind1, 
                               kdm_data_gmv_sub_4year %>% 
                                 select(src_subject_id, eventname, phys_ment_health:gender, 
                                        mri_info_manufacturer))


# Only include those with at least two timepoints
kdm_data_gmv_sub_long_comp <- kdm_data_gmv_sub_long %>%
  group_by(src_subject_id) %>%
  filter(n() == 3) %>%
  ungroup()


```


# Participants Wide Format
```{r}
# Add string names and subset columns ready for cbind
kdm_data_gmv_sub_2year_forBind <- kdm_data_gmv_sub_2year %>% 
                 select(src_subject_id, eventname, phys_ment_health, age, kdm, kdm_advance) %>%
  rename_with(~ paste(.,"_2year", sep = ""), eventname:kdm_advance)


kdm_data_gmv_sub_4year_forBind <- kdm_data_gmv_sub_4year %>% 
                 select(src_subject_id, eventname, phys_ment_health, age, kdm, kdm_advance) %>%
  rename_with(~ paste(.,"_4year", sep = ""), eventname:kdm_advance)



m1 <- left_join(kdm_data_gmv_sub_base %>% 
                 select(src_subject_id, eventname, phys_ment_health:gender, mri_info_manufacturer), 
                kdm_data_gmv_sub_2year_forBind, 
            by = c("src_subject_id"))

kdm_data_gmv_sub_wide <- left_join(m1, 
                               kdm_data_gmv_sub_4year_forBind, 
                               by = c("src_subject_id"))

# Get participants with at least 2 data points
kdm_data_gmv_sub_wide <- kdm_data_gmv_sub_wide %>%
  filter(rowSums(!is.na(select(., "eventname", "eventname_2year", "eventname_4year"))) >= 2)

# Add time in program column
kdm_data_gmv_sub_wide <- kdm_data_gmv_sub_wide %>%
  mutate(time_in_program = case_when(
    rowSums(!is.na(select(., "eventname", "eventname_2year", "eventname_4year"))) == 3 ~ 4,
    rowSums(!is.na(select(., "eventname", "eventname_2year", "eventname_4year"))) >= 2 ~ 2,
    TRUE ~ NA_integer_
  ))

```


# Plot Longitudinal
```{r}
# Participants with at least 2 time points
ggplot(data = kdm_data_gmv_sub_long, 
       aes(x = age, y = kdm, group = src_subject_id, color = as.factor(sex))) +
  geom_point() +                       # Add points
  geom_line() +                        # Add lines connecting points
  labs(x = "Chronological Age", y = "Brain Age", color = "sex") +
  theme_minimal() 

ggplot(data = kdm_data_gmv_sub_long, 
       aes(x = age, y = kdm, group = src_subject_id, color = as.factor(sex))) +
  geom_point() +                       # Add points
  geom_line(alpha = 0.5) +             # Add lines connecting points with lighter color (alpha = 0.5)
  labs(x = "Chronological Age", y = "Brain Age", color = "sex") +
  theme_minimal() +
  facet_wrap(~ as.factor(sex), ncol = 1)  # Separate graphs for female and male

# Participants with 3 time points
ggplot(data = kdm_data_gmv_sub_long_comp, 
       aes(x = age, y = kdm, group = src_subject_id, color = as.factor(sex))) +
  geom_point() +                       # Add points
  geom_line() +                        # Add lines connecting points
  labs(x = "Chronological Age", y = "Brain Age", color = "sex") +
  theme_minimal() 

ggplot(data = kdm_data_gmv_sub_long_comp, 
       aes(x = age, y = kdm, group = src_subject_id, color = as.factor(sex))) +
  geom_point() +                       # Add points
  geom_line(alpha = 0.5) +             # Add lines connecting points with lighter color (alpha = 0.5)
  labs(x = "Chronological Age", y = "Brain Age", color = "sex") +
  theme_minimal() +
  facet_wrap(~ as.factor(sex), ncol = 1)  # Separate graphs for female and male

ggplot(data = kdm_data_gmv_sub_long_comp, 
       aes(x = age, y = kdm_advance, group = src_subject_id, color = as.factor(sex))) +
  geom_point() +                       # Add points
  geom_line(alpha = 0.5) +             # Add lines connecting points with lighter color (alpha = 0.5)
  labs(x = "Chronological Age", y = "KDM Advance", color = "sex") +
  theme_minimal() +
  facet_wrap(~ as.factor(sex), ncol = 1)  # Separate graphs for female and male

```


# Write 2 and 4 Year, and all 3 timepoint KDM Projections
```{r}
write.csv(kdm_data_gmv_sub_2year, paste0(root, "summary_data/kdm_data_gmv_sub_2year.csv"))
write.csv(kdm_data_gmv_sub_4year, paste0(root, "summary_data/kdm_data_gmv_sub_4year.csv"))
write.csv(kdm_data_gmv_sub_long, paste0(root, "summary_data/kdm_data_gmv_sub_long.csv"))
write.csv(kdm_data_gmv_sub_long_comp, paste0(root, "summary_data/kdm_data_gmv_sub_long_comp.csv"))
write.csv(kdm_data_gmv_sub_wide, paste0(root, "summary_data/kdm_data_gmv_sub_wide.csv"))

cor.test(kdm_data_gmv_sub_long_comp$kdm, kdm_data_gmv_sub_long_comp$age)

```


# CORTICAL THICKNESS AND BOTH 

## Read in Data
```{r}
# Cortical Thickness
kdm_train_thk_sub <- readRDS(paste0(root, "/summary_data/kdm_train_thk_sub.rds"))

kdm_data_thk_sub_base <- read.csv(paste0(root, "Version5.0_Exported_Data/kdm_data_thk_sub.csv"))

thk_sub_2year <- read.csv(paste0(root, "Version5.0_Exported_Data/thk_sub_2year.csv"))
thk_sub_4year <- read.csv(paste0(root, "Version5.0_Exported_Data/thk_sub_4year.csv"))

thk_markers_sub <- colnames(thk_sub_2year %>% select(contains("smri")))


# Both
kdm_train_gmv_thk_sub <- readRDS(paste0(root, "/summary_data/kdm_train_gmv_thk_sub.rds"))

kdm_data_gmv_thk_sub_base <- read.csv(paste0(root, "Version5.0_Exported_Data/kdm_data_gmv_thk_sub.csv"))

gmv_thk_sub_2year <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_thk_sub_2year.csv"))
gmv_thk_sub_4year <- read.csv(paste0(root, "Version5.0_Exported_Data/gmv_thk_sub_4year.csv"))

gmv_thk_markers_sub <- colnames(kdm_data_gmv_thk_sub_base %>% select(contains("smri")))


```

## Function to Project KDM Data
```{r}
project_kdm_data <- function(data_base, data_2year, data_4year, fit_model, markers) {
  library(dplyr)
  
  data_2year$gender <- data_2year$sex
  
  # Project to 2 Year
  kdm_bbb_sub_2year <- kdm_calc(data_2year, biomarkers = markers, fit = fit_model$fit, 
                                s_ba2 = fit_model$fit$s_ba2)
  kdm_data_bbb_sub_2year <- kdm_bbb_sub_2year$data
  
  data_4year$gender <- data_4year$sex

  
  data_base <- data_base %>% select(-starts_with("X"))
  kdm_data_bbb_sub_2year <- kdm_data_bbb_sub_2year %>% select(-starts_with("X"))
  
  # Project to 4 Year
  kdm_bbb_sub_4year <- kdm_calc(data_4year, biomarkers = markers, fit = fit_model$fit, 
                                s_ba2 = fit_model$fit$s_ba2)
  kdm_data_bbb_sub_4year <- kdm_bbb_sub_4year$data
  
  kdm_data_bbb_sub_4year <- kdm_data_bbb_sub_4year %>% select(-starts_with("X"))
  
  # Participants with at least 2 Timepoints (Long)
  bind1 <- rbind(data_base %>% select(src_subject_id, eventname, all_of(markers), 
                                      phys_ment_health:gender, kdm, kdm_advance),
                 kdm_data_bbb_sub_2year %>% select(src_subject_id, eventname, all_of(markers), 
                                                   phys_ment_health:gender, kdm, kdm_advance))
  
  
  kdm_data_bbb_sub_long <- rbind(bind1, 
                                 kdm_data_bbb_sub_4year %>% select(src_subject_id, eventname, 
                                                                   all_of(markers), 
                                                                   phys_ment_health:gender, 
                                                                   kdm, kdm_advance))
  
  # Only include those with at least two timepoints
  kdm_data_bbb_sub_long_comp <- kdm_data_bbb_sub_long %>%
    group_by(src_subject_id) %>%
    filter(n() >= 2) %>%
    ungroup()
  
  # Bind all time points together
  kdm_data_bbb_all <- rbind(rbind(data_base, kdm_data_bbb_sub_2year), kdm_data_bbb_sub_4year)
  
  return(list(kdm_2year = kdm_data_bbb_sub_2year,
              kdm_4year = kdm_data_bbb_sub_4year,
              kdm_all = kdm_data_bbb_all,
              kdm_comp = kdm_data_bbb_sub_long_comp))
}




```



## Project Cortical Thickness and Both
```{r}

thk_proj <- project_kdm_data(
  data_base = kdm_data_thk_sub_base,
  data_2year = thk_sub_2year,
  data_4year = thk_sub_4year,
  fit_model = kdm_train_thk_sub,
  markers = thk_markers_sub
)

thk_2year_data <- thk_proj$kdm_2year
thk_4year_data <- thk_proj$kdm_4year
thk_all_year_data <- thk_proj$kdm_all
thk_comp_data <- thk_proj$kdm_comp

gmv_thk_proj <- project_kdm_data(
  data_base = kdm_data_gmv_thk_sub_base,
  data_2year = gmv_thk_sub_2year,
  data_4year = gmv_thk_sub_4year,
  fit_model = kdm_train_gmv_thk_sub,
  markers = gmv_thk_markers_sub
)

gmv_thk_2year_data <- gmv_thk_proj$kdm_2year
gmv_thk_4year_data <- gmv_thk_proj$kdm_4year
gmv_thk_all_year_data <- gmv_thk_proj$kdm_all
gmv_thk_comp_data <- gmv_thk_proj$kdm_comp

```

## Metrics Thickness and GMV
### 2 year
```{r}
nrow(gmv_thk_2year_data)
cor.test(as.numeric(gmv_thk_2year_data$kdm), as.numeric(gmv_thk_2year_data$age))
Metrics::rmse(as.numeric(gmv_thk_2year_data$kdm), as.numeric(gmv_thk_2year_data$age))
Metrics::mae(as.numeric(gmv_thk_2year_data$kdm), as.numeric(gmv_thk_2year_data$age))


gmv_thk_2year_data$gender <- as.factor(gmv_thk_2year_data$sex)
plot_ba(gmv_thk_2year_data, "kdm", "KDM\nBiological Age")

```




## Export 
```{r}
write.csv(thk_2year_data, paste0(root, "Version5.0_Exported_Data/thk_2year_data.csv"))
write.csv(thk_4year_data, paste0(root, "Version5.0_Exported_Data/thk_4year_data.csv"))
write.csv(thk_all_year_data, paste0(root, "Version5.0_Exported_Data/thk_all_year_data.csv"))
write.csv(thk_comp_data, paste0(root, "Version5.0_Exported_Data/thk_comp_data.csv"))

write.csv(gmv_thk_2year_data, paste0(root, "Version5.0_Exported_Data/gmv_thk_2year_data.csv"))
write.csv(gmv_thk_4year_data, paste0(root, "Version5.0_Exported_Data/gmv_thk_4year_data.csv"))
write.csv(gmv_thk_all_year_data, paste0(root, "Version5.0_Exported_Data/gmv_thk_all_year_data.csv"))
write.csv(gmv_thk_comp_data, paste0(root, "Version5.0_Exported_Data/gmv_thk_comp_data.csv"))


```











