---
title: "KDM_THK_5.0_V1"
format:
  html: 
    theme: cosmo
    fontsize: 1.1em
    linestretch: 1.7
toc: true
editor: visual
---

This file runs the first iteration of KDM Cortical Thickness analyses by training on baseline. Reads in subsetted Cortical Thickness ROIs

Input: + thk_sub.csv

Output: + kdm_train_thk_sub.rds (Trained model) + (Projected KDM values for baseline)

1.  Read in data and split into healthy and unhealthy
2.  Split into time points
3.  Split healthy into training and test
4.  Train healthy
5.  Test healthy
6.  Project to unhealthy group
7.  T-Test
8.  Write csv file

# Libraries

```{r}
#install.packages("flexsurv")
#devtools::install_github("dayoonkwon/BioAge")
library(BioAge)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(stats)
library(skimr)
library(pcaPP)
library(stringr)
library(stats)
library(misty)
library(emmeans)
```

# Read in Data

```{r}
thk <- read.csv(paste0(root, "Version5.0_Exported_Data/thk_sub_flip.csv"))

# thk <- read.csv(paste0(root, "Version5.0_Exported_Data/thk_sub_base.csv"))

colnames(thk)

```

# Split Baseline into healthy and unhealthy

```{r}
thk_healthy <- thk %>% filter(eventname == "baseline_year_1_arm_1") %>% filter(phys_ment_health == 0)
thk_unhealthy <- thk %>% filter(eventname == "baseline_year_1_arm_1") %>% filter(phys_ment_health != 0)

nrow(thk_healthy)
nrow(thk_unhealthy)
```

# Split Healthy Group for baseline

```{r}
set.seed(18)

### Healthy Training ###
samp <- sample(c(TRUE, FALSE), nrow(thk_healthy), replace=TRUE, prob=c(0.4,0.6))
thk_train <- thk_healthy[samp, ]
thk_test <- thk_healthy[!samp, ]

nrow(thk_train) # 1085
nrow(thk_test) # 2490
```

# Train Healthy

```{r}
brain_markers_sub <- colnames(thk_train %>% select(contains("smri")))

kdm_train_thk_sub <- kdm_calc(thk_train, biomarkers = brain_markers_sub)

saveRDS(kdm_train_thk_sub, file = "/Users/hansoochang/Drexel/ABCD/summary_data/kdm_train_thk_sub.rds")
```

#Correlation tests between kdm_age and chronological age

```{r}
nrow(kdm_train_thk_sub$data)
hist(kdm_train_thk_sub$data$age)
cor.test(as.numeric(kdm_train_thk_sub$data$kdm), as.numeric(kdm_train_thk_sub$data$age))
Metrics::rmse(as.numeric(kdm_train_thk_sub$data$kdm), as.numeric(kdm_train_thk_sub$data$age))
Metrics::mae(as.numeric(kdm_train_thk_sub$data$kdm), as.numeric(kdm_train_thk_sub$data$age))

```

# Project to test

```{r}
kdm_test_thk_sub_test <- kdm_calc(thk_test, biomarkers = brain_markers_sub, 
                                  fit = kdm_train_thk_sub$fit, s_ba2 = 
                       kdm_train_thk_sub$fit$s_ba2)

kdm_data_thk_sub_test <- kdm_test_thk_sub_test$data
```

# Correlation tests between kdm_age (both genders) and chronological age

```{r}
nrow(kdm_data_thk_sub_test)
cor.test(as.numeric(kdm_data_thk_sub_test$kdm), as.numeric(kdm_data_thk_sub_test$age))
Metrics::rmse(as.numeric(kdm_data_thk_sub_test$kdm), as.numeric(kdm_data_thk_sub_test$age))
Metrics::mae(as.numeric(kdm_data_thk_sub_test$kdm), as.numeric(kdm_data_thk_sub_test$age))

kdm_data_thk_sub_test$gender <- as.factor(kdm_data_thk_sub_test$sex)
#plot age vs bioage
plot_ba(kdm_data_thk_sub_test, "kdm", "KDM\nBiological Age")

```

# Project trained model onto Unhealthy cohort

## Get prediction

```{r}

kdm_unhealthy_thk_sub <- kdm_calc(thk_unhealthy, 
                                    biomarkers = brain_markers_sub, 
                                    fit = kdm_train_thk_sub$fit, 
                                    s_ba2 = kdm_train_thk_sub$fit$s_ba2)

kdm_data_unhealthy_thk_sub <- kdm_unhealthy_thk_sub$data 


```

# Correlation test between KDM age and Chronological Age for Unhealthy cohort

```{r}
nrow(kdm_data_unhealthy_thk_sub)
cor.test(as.numeric(kdm_data_unhealthy_thk_sub$kdm), as.numeric(kdm_data_unhealthy_thk_sub$age))
Metrics::rmse(as.numeric(kdm_data_unhealthy_thk_sub$kdm), as.numeric(kdm_data_unhealthy_thk_sub$age))
Metrics::mae(as.numeric(kdm_data_unhealthy_thk_sub$kdm), as.numeric(kdm_data_unhealthy_thk_sub$age))


kdm_data_unhealthy_thk_sub$gender <- as.factor(kdm_data_unhealthy_thk_sub$sex)
plot_ba(kdm_data_unhealthy_thk_sub, "kdm", "KDM\nBiological Age")

```

# Test for Normality for KDM

```{r}
# variances are approximately = 1

# KDM Biological Age
shapiro.test(kdm_data_thk_sub_test$kdm)
#shapiro.test(kdm_data_unhealthy_thk_sub$kdm)

ggdensity(kdm_data_thk_sub_test$kdm)
ggdensity(kdm_data_unhealthy_thk_sub$kdm)
ggdensity(kdm_data_thk_sub_test$age) 

ggqqplot(kdm_data_thk_sub_test$kdm)
ggqqplot(kdm_data_unhealthy_thk_sub$kdm)

hist(kdm_data_thk_sub_test$kdm, xlab = "KDM Value")
hist(kdm_data_thk_sub_test$kdm_advance, xlab = "KDM Advance Value")

hist(kdm_data_unhealthy_thk_sub$kdm, xlab = "KDM Value")
hist(kdm_data_unhealthy_thk_sub$kdm_advance, xlab = "KDM Advance Value")
```

# T-Test

```{r}
sd(kdm_data_thk_sub_test$kdm)
sd(kdm_data_unhealthy_thk_sub$kdm)

sd(kdm_data_thk_sub_test$kdm_advance)
sd(kdm_data_unhealthy_thk_sub$kdm_advance)

# T-Test for average healthy KDM and unhealthy KDM
t.test(kdm_data_thk_sub_test$kdm, kdm_data_unhealthy_thk_sub$kdm,
       alternative = "two.sided", var.equal = T)

# T-Test for average healthy KDM_advance and unhealthy KDM_advance
t.test(kdm_data_thk_sub_test$kdm_advance, kdm_data_unhealthy_thk_sub$kdm_advance, 
       alternative = "two.sided", var.equal = T)

# t.test between chronological ages
t.test(kdm_data_thk_sub_test$age, kdm_data_unhealthy_thk_sub$age, 
       alternative = "two.sided", var.equal = TRUE)

```

# Write Baseline Projections

```{r}
# Merge Test and Unhealhty cohort
kdm_data_thk_sub <- rbind(kdm_data_thk_sub_test, kdm_data_unhealthy_thk_sub)

write.csv(kdm_data_thk_sub, paste0(root, "Version5.0_Exported_Data/kdm_data_thk_sub.csv"))

```
