---
title: "KDM_BBB_5.0_V1"
output: html_document
date: "2023-08-24"
---

This file runs the first iteration of KDM analyses by training on baseline for Blood-Based Biomarkers (BBB). Reads in standardized Blood-Based Biomarker data

Input:
+ bbb_sub.csv

Output:
+ kdm_train_bbb_sub.rds (Trained model)
+ (Projected KDM values for baseline) 

1. Read in data and split into healthy and unhealthy
2. Split into time points
3. Split healthy into training and test
4. Train healthy
5. Test healthy
6. Project to unhealthy group
7. T-Test 
9. Write csv file


# Libraries
```{r}
#install.packages("flexsurv")
#devtools::install_github("dayoonkwon/BioAge")
library(BioAge)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(stats)
library(skimr)
library(pcaPP)
library(stringr)
library(stats)
library(misty)
library(emmeans)
```


# Read in Data
```{r}
bbb <- read.csv(paste0(root, "Version5.0_Exported_Data/bbb_all_flipped.csv"))
table(bbb$eventname)
bbb %>% filter(eventname == "2_year_follow_up_y_arm_1") %>% filter(phys_ment_health == 0)
bbb %>% filter(eventname == "2_year_follow_up_y_arm_1") %>% filter(phys_ment_health > 0)

```


# Split Baseline into healthy and unhealthy
```{r}

bbb %>% 
  filter(eventname == "2_year_follow_up_y_arm_1") %>% skim()

bbb_healthy_2year <- bbb %>% 
  filter(eventname == "2_year_follow_up_y_arm_1") %>% 
  filter(phys_ment_health == 0)

bbb_unhealthy_2year <- bbb %>% 
  filter(eventname == "2_year_follow_up_y_arm_1") %>% 
  filter(phys_ment_health != 0)

bbb_healthy_2year %>% select(biospec_blood_hemoglobin_a1:PLR)  %>%
  complete.cases() %>%
  sum() # Sum the TRUE values to get the count

nrow(bbb_healthy_2year) # 448
nrow(bbb_unhealthy_2year) # 187

bbb_healthy_2year$age

```

# Split Healthy Group for baseline
```{r}
set.seed(18)

### Healthy Training ###
samp <- sample(c(TRUE, FALSE), nrow(bbb_healthy_2year), replace=TRUE, prob=c(0.5,0.5))
bbb_train <- bbb_healthy_2year[samp, ]
bbb_test <- bbb_healthy_2year[!samp, ]

bbb_train %>% select(biospec_blood_hemoglobin_a1:PLR)  %>%
  complete.cases() %>%
  sum()

nrow(bbb_train) # 221
nrow(bbb_test) # 227
```

# Train Healthy
```{r}

bbb_markers_sub <- colnames(bbb_train %>% select(biospec_blood_hemoglobin_a1:PLR))


kdm_train_bbb_sub <- kdm_calc(bbb_train, biomarkers = bbb_markers_sub)

saveRDS(kdm_train_bbb_sub, paste0(root, "Version5.0_Exported_Data/kdm_train_bbb_sub.rds"))
```

# Correlation tests between kdm_age and chronological age
```{r}
nrow(kdm_train_bbb_sub$data)
hist(kdm_train_bbb_sub$data$age)
cor.test(as.numeric(kdm_train_bbb_sub$data$kdm), as.numeric(kdm_train_bbb_sub$data$age))

# Calculate RMSE
rmse_manual <- sqrt(mean((as.numeric(kdm_train_bbb_sub$data$kdm) - 
                            as.numeric(kdm_train_bbb_sub$data$age))^2, na.rm = T))

# Calculate MAE
mae_manual <- mean(abs(as.numeric(kdm_train_bbb_sub$data$kdm) - as.numeric(kdm_train_bbb_sub$data$age)),
                   na.rm = T)


# Print the results
print(paste("Manual RMSE:", rmse_manual))
print(paste("Manual MAE:", mae_manual))
```


# Project to test
## Get Prediction
```{r}
kdm_test_bbb_sub_test <- kdm_calc(bbb_test, biomarkers = bbb_markers_sub, fit = kdm_train_bbb_sub$fit, s_ba2 = 
                       kdm_train_bbb_sub$fit$s_ba2)

kdm_data_bbb_sub_test <- kdm_test_bbb_sub_test$data

nrow(kdm_data_bbb_sub_test)
range(kdm_data_bbb_sub_test$age)

```


## Correlation tests between kdm_age (both genders) and chronological age
```{r}
nrow(kdm_data_bbb_sub_test)
cor.test(as.numeric(kdm_data_bbb_sub_test$kdm), as.numeric(kdm_data_bbb_sub_test$age))
# Calculate RMSE
rmse_manual <- sqrt(mean((as.numeric(kdm_data_bbb_sub_test$kdm) - 
                            as.numeric(kdm_data_bbb_sub_test$age))^2, na.rm = T))

# Calculate MAE
mae_manual <- mean(abs(as.numeric(kdm_data_bbb_sub_test$kdm) - 
                         as.numeric(kdm_data_bbb_sub_test$age)),
                   na.rm = T)

mean(kdm_data_bbb_sub_test$kdm, na.rm = T)
sd(kdm_data_bbb_sub_test$kdm, na.rm = T)

# Print the results
print(paste("Manual RMSE:", rmse_manual))
print(paste("Manual MAE:", mae_manual))

```

# Project trained model onto Unhealthy cohort
## Get prediction
```{r}
kdm_unhealthy_bbb <- kdm_calc(bbb_unhealthy_2year, biomarkers = bbb_markers_sub, 
                              fit = kdm_train_bbb_sub$fit, s_ba2 = kdm_train_bbb_sub$fit$s_ba2)

kdm_data_unhealthy_bbb <- kdm_unhealthy_bbb$data

nrow(kdm_data_unhealthy_bbb)
```

## Correlation tests between kdm_age (both genders) and chronological age (Unhealthy)
```{r}
nrow(kdm_data_unhealthy_bbb)
cor.test(as.numeric(kdm_data_unhealthy_bbb$kdm), as.numeric(kdm_data_unhealthy_bbb$age))
# Calculate RMSE
rmse_manual <- sqrt(mean((as.numeric(kdm_data_unhealthy_bbb$kdm) - 
                            as.numeric(kdm_data_unhealthy_bbb$age))^2, na.rm = T))

# Calculate MAE
mae_manual <- mean(abs(as.numeric(kdm_data_unhealthy_bbb$kdm) - 
                         as.numeric(kdm_data_unhealthy_bbb$age)),
                   na.rm = T)
mean(kdm_data_unhealthy_bbb$kdm, na.rm = T)
sd(kdm_data_unhealthy_bbb$kdm, na.rm = T)

# Print the results
print(paste("Manual RMSE:", rmse_manual))
print(paste("Manual MAE:", mae_manual))

```


# Plot kdm_advance
```{r}
#plot age vs bioage
plot_ba(kdm_data_bbb_sub, "kdm_advance", "KDM\nBiological Age")
ggdensity(kdm_data_bbb_sub$kdm_advance)

hist(kdm_data_bbb_sub$kdm)
hist(kdm_data_bbb_sub$kdm_advance)

hist(kdm_data_unhealthy$kdm)
hist(kdm_data_unhealthy$kdm_advance)

```

# Export Data
```{r}
# Merge Test and Unhealhty cohort
kdm_data_bbb_sub_baseline <- rbind(kdm_data_bbb_sub_test, kdm_data_unhealthy_bbb) 
table(kdm_data_bbb_sub$phys_ment_health)

sd(kdm_data_bbb_sub_baseline$kdm_advance, na.rm = T)

nrow(kdm_data_bbb_sub_baseline)

write.csv(kdm_data_bbb_sub_baseline, paste0(root, "Version5.0_Exported_Data/kdm_data_bbb_sub_baseline.csv"))

```







