---
title: "ParentQuestionnaire"
output: pdf_document
date: "2022-11-18"
---

# Libraries
```{r}
library(skimr)
library(matrixStats)
```


# Read in data
## Parent Survey
```{r}
#parent <- read.delim("/Users/hansoochang/Drexel/ABCD/data/abcd_ksad01.txt",sep="", fill = TRUE)

# Version 5.1 Data
parent <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/mental-health/mh_p_ksads_ss.csv")
head(parent)

# parent <- parent[-1,]# Take out first row

# colnames(parent)

parent[parent == ""] <- NA

table(parent$eventname)

# parentb <- parent[which(parent$eventname == "baseline_year_1_arm_1"), ]
# parent1 <- parent[which(parent$eventname == "1_year_follow_up_y_arm_1"), ]
# parent2 <- parent[which(parent$eventname == "2_year_follow_up_y_arm_1"), ]

p_list <- c("src_subject_id", "eventname","ksads_1_843_p", "ksads_1_845_p", "ksads_1_844_p", 
            "ksads_1_840_p", "ksads_1_841_p", "ksads_1_842_p", "ksads_1_847_p", 
            "ksads_1_846_p", "ksads_2_837_p", "ksads_2_835_p", "ksads_2_836_p", 
            "ksads_2_836_p", "ksads_2_831_p", "ksads_2_832_p", "ksads_2_830_p", 
            "ksads_2_833_p", "ksads_2_834_p", "ksads_2_839_p", "ksads_2_838_p", 
            "ksads_3_848_p", "ksads_4_851_p", "ksads_4_852_p", "ksads_4_826_p",
            "ksads_4_827_p", "ksads_4_829_p", "ksads_4_828_p", "ksads_4_850_p",
            "ksads_4_849_p", "ksads_5_906_p", "ksads_5_907_p", "ksads_5_857_p",
            "ksads_5_858_p", "ksads_6_859_p", "ksads_6_860_p", "ksads_7_861_p",
            "ksads_7_909_p", "ksads_7_910_p", "ksads_7_862_p", "ksads_8_864_p", 
            "ksads_8_863_p", "ksads_8_912_p", "ksads_8_911_p", "ksads_9_868_p", 
            "ksads_9_867_p", "ksads_10_869_p", "ksads_10_870_p", "ksads_11_917_p",
            "ksads_11_918_p", "ksads_11_919_p", "ksads_11_920_p", "ksads_12_928_p",
            "ksads_12_927_p", "ksads_12_925_p", "ksads_12_926_p", "ksads_13_939_p",
            "ksads_13_938_p", "ksads_13_929_p", "ksads_13_934_p", "ksads_13_933_p", 
            "ksads_13_932_p", "ksads_13_931_p", "ksads_13_930_p", "ksads_13_936_p",
            "ksads_13_935_p", "ksads_13_937_p", "ksads_13_940_p", "ksads_13_943_p",
            "ksads_13_942_p", "ksads_13_944_p", "ksads_13_941_p", "ksads_14_856_p",
            "ksads_14_855_p", "ksads_14_853_p", "ksads_14_854_p", "ksads_17_905_p",
            "ksads_17_904_p", "ksads_18_903_p", "ksads_19_895_p", "ksads_19_896_p",
            "ksads_19_891_p", "ksads_19_892_p", "ksads_20_893_p", "ksads_20_894_p", 
            "ksads_20_874_p", "ksads_20_883_p", "ksads_20_872_p", "ksads_20_881_p", 
            "ksads_20_889_p", "ksads_20_890_p", "ksads_20_887_p", "ksads_20_878_p",
            "ksads_20_877_p", "ksads_20_886_p", "ksads_20_875_p", "ksads_20_884_p",
            "ksads_20_876_p", "ksads_20_885_p", "ksads_20_879_p", "ksads_20_888_p",
            "ksads_20_873_p", "ksads_20_882_p", "ksads_20_880_p", "ksads_20_871_p",
            "ksads_21_923_p", "ksads_21_924_p", "ksads_21_921_p", "ksads_21_922_p",
            "ksads_23_946_p", "ksads_25_916_p", "ksads_25_915_p", "ksads_25_866_p", "ksads_25_865_p")

# Parent Survey 
parent %>%
  select(one_of(p_list)) %>%
  mutate_at(vars(ksads_1_843_p:ksads_25_865_p), as.factor) %>%
  skim()

p_ksads <- parent %>%
  select(one_of(p_list)) %>%
  mutate_at(vars(ksads_1_843_p:ksads_25_865_p), as.factor)
```


## Child Survey
```{r}

# Version 5.1 Data
child <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/mental-health/mh_y_ksads_ss.csv")

# child <- child[-1,]# Take out first row

child[child == ""] <- NA

table(child$eventname)


child %>% select(src_subject_id,eventname,
                 ksads_4_826_t:ksads_22_970_t, ksads2_19_849_t:ksads2_19_854_t, 
                 ksads2_21_881_t:ksads2_21_885_t, ksads2_22_929_t:ksads2_22_930_t,
                 ksads2_23_919_t:ksads2_23_926_t, ksads2_24_927_t:ksads2_23_918_t, 
                 ksads2_25_823_t:ksads2_25_876_t, ksads2_23_905_t:ksads2_23_917_t,
                 ksads2_20_843_t:ksads2_20_842_t, ksads2_20_844_t:ksads2_20_852_t,
                 ksads2_5_814_t:ksads2_5_867_t, ksads2_6_817_t:ksads2_6_868_t, ksads2_4_807_t,
                 ksads2_4_805_t:ksads2_4_806_t, ksads2_4_808_t, ksads2_8_821_t:ksads2_8_872_t,
                 ksads2_9_825_t:ksads2_9_826_t, ksads2_7_870_t, ksads2_7_819_t:ksads2_7_869_t,
                 ksads2_1_796_t, ksads2_1_790_t:ksads2_1_795_t, ksads2_1_797_t,
                 ksads2_2_803_t:ksads2_2_933_t, ksads2_3_804_t:ksads2_2_802_t,
                 ksads2_2_798_t:ksads2_15_860_t, ksads2_15_859_t, ksads2_14_811_t, 
                 ksads2_14_809_t:ksads2_14_810_t, ksads2_14_812_t:ksads2_14_813_t, 
                 ksads2_18_861_t:ksads2_18_863_t, ksads2_16_855_t:ksads2_16_858_t, ksads2_17_864_t,
                 ksads2_17_865_t, ksads2_11_877_t:ksads2_11_880_t, ksads2_12_886_t:ksads2_12_889_t,
                 ksads2_10_827_t:ksads2_10_874_t, ksads2_13_904_t, ksads2_13_902_t, 
                 ksads2_13_890_t:ksads2_13_1000_t)  %>%
  mutate_at(vars(ksads_4_826_t:ksads2_13_1000_t), as.factor) %>%
  skim()
```



### CBCL ###

t-score is total score, with a higher score indicating more depressive symptoms
```{r}
cbcl <- read.delim("/Users/hansoochang/Drexel/ABCD/data/abcd_cbcls01.txt", sep="", fill = TRUE)

skim(cbcl)

```

## Get only total scores
```{r}
cbcl_t <- cbcl %>% dplyr::select(contains(c("_t", "subjectkey", "eventname", "interview_age")))
cbcl_t <- cbcl_t[-1, ]

skim(cbcl_t)
```

The broadband Internalizing Domain is a measure of emotional problems and contains three syndrome scales: Anxious/Depressed, Withdrawn/Depressed, and Somatic Complaints. The broadband Externalizing Domain measures behavioral problems and contains the Rule Breaking Behavior and Aggressive Behavior syndrome scales. Three other syndrome scales do not belong to either broadband scale: Social Problems, Thought Problems, and Attention Problems.

“Clinically significant” elevations are indicated by T-scores ≥ 64 on the broadband scales and ≥70 on the syndrome scales. “Borderline” elevations range from 60 to 63 and 65 to 69 on the broadband and syndrome scales, respectively.


# Subset BA patients
## Biological Age
```{r}
bm <- read.csv("/Users/hansoochang/Drexel/ABCD/data/biomarkers.csv")
head(bm)
head(cbcl_t)

bm_cbcl <- merge(bm, cbcl_t, by.x = c("subjectkey", "eventname.y"), by.y = c("subjectkey", "eventname"))

# remove some unnecessary columns
bm_cbcl <- subset(bm_cbcl, select = -c(`cbcl_scr_syn_thought_m`, `cbcl_scr_syn_thought_nm`
                                       , `cbcl_scr_syn_thought_r`,`cbcl_scr_syn_totprob_m`,
                                       `cbcl_scr_syn_totprob_nm`, `cbcl_scr_syn_totprob_r`))

skim(bm_cbcl)
```

# Brain Age
## GMV
```{r}
### Desikan Atlas
### CBCL ###
# bm_brain <- read.csv("/Users/hansoochang/Drexel/ABCD/data/smrip_gmv_y2.csv")
bm_brain <- read.csv("/Users/hansoochang/Drexel/ABCD/abcd-data-release-5.1/core/imaging/mri_y_smr_vol_dsk.csv")
head(bm_brain)
head(cbcl_t)

cbcl_t$src_subject_id <- cbcl_t$subjectkey

# GMV and CBCL Merge
bm_brain_cbcl <- merge(bm_brain, cbcl_t, by = c("src_subject_id", "eventname"))
bm_brain_cbcl %>% filter(eventname == "baseline_year_1_arm_1")

# GMV and KSADS merge
bm_brain_ksads <- merge(bm_brain, p_ksads, by = c("src_subject_id", "eventname"))

# remove some unnecessary columns
bm_brain_cbcl <- subset(bm_brain_cbcl, select = -c(`cbcl_scr_syn_thought_m`, `cbcl_scr_syn_thought_nm`
                                       , `cbcl_scr_syn_thought_r`,`cbcl_scr_syn_totprob_m`,
                                       `cbcl_scr_syn_totprob_nm`, `cbcl_scr_syn_totprob_r`))




### Destrieux Parcellation

# bm_brain <- read.csv("/Users/hansoochang/Drexel/ABCD/data/stand_dest_vol_y2.csv")
# head(bm_brain)
# head(cbcl_t)
# 
# bm_brain_cbcl <- merge(bm_brain, cbcl_t, by = c("subjectkey", "eventname"))
# 
# # remove some unnecessary columns
# bm_brain_cbcl <- subset(bm_brain_cbcl, select = -c(`cbcl_scr_syn_thought_m`, `cbcl_scr_syn_thought_nm`
#                                        , `cbcl_scr_syn_thought_r`,`cbcl_scr_syn_totprob_m`,
#                                        `cbcl_scr_syn_totprob_nm`, `cbcl_scr_syn_totprob_r`))
# 
# skim(bm_brain_cbcl)
```

# Cortical Thickness
```{r}
bm_cortthick <- read.csv("/Users/hansoochang/Drexel/ABCD/data/smrip_cortthick_y2.csv")
#head(bm_brain)
#head(cbcl_t)

bm_cortthick_cbcl <- merge(bm_cortthick, cbcl_t, by = c("subjectkey", "eventname"))

# remove some unnecessary columns
bm_cortthick_cbcl <- subset(bm_cortthick_cbcl, select = -c(`cbcl_scr_syn_thought_m`, `cbcl_scr_syn_thought_nm`
                                       , `cbcl_scr_syn_thought_r`,`cbcl_scr_syn_totprob_m`,
                                       `cbcl_scr_syn_totprob_nm`, `cbcl_scr_syn_totprob_r`))

skim(bm_cortthick_cbcl)
```



# Complete cases 
## Bio Age
```{r}

bm_cbcl <- bm_cbcl[complete.cases(bm_cbcl),]
bm_cbcl[, 37:56] <- as.numeric(unlist(bm_cbcl[, 37:56]))
bm_cbcl[, 37:56]

```

## Brain Age
# GMV
```{r}
bm_brain_cbcl %>% filter(eventname == "baseline_year_1_arm_1") %>% skim()
bm_brain_cbcl %>% filter(eventname == "baseline_year_1_arm_1")
# CBCL
bm_brain_cbcl[bm_brain_cbcl == ""] <- NA
bm_brain_cbcl <- bm_brain_cbcl[complete.cases(bm_brain_cbcl),]
skim(bm_brain_cbcl) # 18457

```


# Cortical Thickness
```{r}
bm_cortthick_cbcl[bm_cortthick_cbcl == ""] <- NA
bm_cortthick_cbcl <- bm_cortthick_cbcl[complete.cases(bm_cortthick_cbcl),]
skim(bm_cortthick_cbcl) # 5383

```


Clinical range is above t score of 67
https://link.springer.com/article/10.1007/s10862-010-9198-1

Clinical range is above t score of 60...
https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0250235#pone.0250235.ref043

Clinical cutoff is greater than 66
https://osf.io/gzybv

# Find all that are above t-score of 67
## Bio Age
```{r}
library(Hmisc)
bm_cbcl_t <- bm_cbcl[, c(1:2, 37:56)]
summary(bm_cbcl_t)
bm_cbcl_t_bin <- ifelse(bm_cbcl_t[, -c(1:2)] > 67, 1, 0)
bm_cbcl_t_bin <- cbind(bm_cbcl_t[,1:2], bm_cbcl_t_bin)

as.data.frame(mapply(table, as.data.frame(bm_cbcl_t_bin)))

hist.data.frame(bm_cbcl_t[1:10])
hist.data.frame(bm_cbcl_t[11:20])

```

## Brain Age
# GMV
```{r}
# CBCL
colnames(bm_brain_cbcl)
bm_brain_cbcl_t <- bm_brain_cbcl %>% select(contains(c("subjectkey", "eventname", "cbcl")))
bm_brain_cbcl_t

bm_brain_cbcl_t_bin <- ifelse(bm_brain_cbcl_t[, -c(1:2)] > 67, 1, 0)
bm_brain_cbcl_t_bin <- cbind(bm_brain_cbcl_t[,1:2], bm_brain_cbcl_t_bin)

bm_brain_cbcl_t_bin <- ifelse(bm_brain_cbcl %>% select(contains(c("cbcl"))) > 67, 1, 0)
bm_brain_cbcl_t_bin <- cbind(bm_brain_cbcl %>% select(contains(c("subjectkey", "eventname", "smri"))), bm_brain_cbcl_t_bin)

as.data.frame(bm_brain_cbcl_t_bin)


# KSADS


```


# distributions of cbcl
```{r}
cbcl_list <- colnames(bm_brain_cbcl_t %>% select(contains("cbcl")))
bm_brain_cbcl_t_num <- bm_brain_cbcl_t %>% mutate_at(vars(contains("cbcl")), as.numeric)

for (cbcl in 1:length(cbcl_list)) {
  hist(bm_brain_cbcl_t_num[, cbcl_list[cbcl]], xlab = cbcl_list[cbcl])
}

```



# Cortical Thickness
```{r}
colnames(bm_cortthick_cbcl)
bm_cortthick_cbcl_t <- bm_cortthick_cbcl %>% select(contains(c("subjectkey", "eventname", "cbcl")))
bm_cortthick_cbcl_t

bm_cortthick_cbcl_t_bin <- ifelse(bm_cortthick_cbcl_t[, -c(1:2)] > 67, 1, 0)
bm_cortthick_cbcl_t_bin <- cbind(bm_cortthick_cbcl_t[,1:2], bm_cortthick_cbcl_t_bin)

bm_cortthick_cbcl_t_bin
```



# Split into cognitively healthy vs. cognitively not healthy
## Bio Age
```{r}
bm_cbcl_t_bin <- as.data.frame(bm_cbcl_t_bin)
bm_cbcl_t_bin$count <- rowSums(bm_cbcl_t_bin == 1)

healthy_cbcl <- bm_cbcl_t_bin[which(bm_cbcl_t_bin$count == 0), ]
unhealthy_cbcl <- bm_cbcl_t_bin[which(bm_cbcl_t_bin$count != 0), ]


nrow(healthy_cbcl)
nrow(unhealthy_cbcl)

write.csv(bm_cbcl_t_bin, "/Users/hansoochang/Drexel/ABCD/data/bm_cbcl_67.csv")
write.csv(healthy_cbcl, file = "/Users/hansoochang/Drexel/ABCD/data/healthy_cbcl_67.csv")
write.csv(unhealthy_cbcl, "/Users/hansoochang/Drexel/ABCD/data/unhealthy_cbcl_67.csv")
```



## Brain Age
# GMV
```{r}
bm_brain_cbcl_t_bin <- as.data.frame(bm_brain_cbcl_t_bin)
bm_brain_cbcl_t_bin$count <- rowSums(bm_brain_cbcl_t_bin == 1)

healthy_cbcl_brain <- bm_brain_cbcl_t_bin[which(bm_brain_cbcl_t_bin$count == 0), ]
unhealthy_cbcl_brain <- bm_brain_cbcl_t_bin[which(bm_brain_cbcl_t_bin$count != 0), ]


nrow(healthy_cbcl_brain) # 4212
nrow(unhealthy_cbcl_brain) # 949



write.csv(bm_brain_cbcl_t_bin, "/Users/hansoochang/Drexel/ABCD/data/bm_brain_cbcl_67.csv")
write.csv(healthy_cbcl_brain, file = "/Users/hansoochang/Drexel/ABCD/data/healthy_cbcl_brain_67.csv")
write.csv(unhealthy_cbcl_brain, "/Users/hansoochang/Drexel/ABCD/data/unhealthy_cbcl_brain_67.csv")
```

# See densities between healhty and unhealthy
```{r}
all_cbcl_gmv <- rbind(healthy_cbcl_brain, unhealthy_cbcl_brain)
all_cbcl_gmv$health <- ifelse(all_cbcl_gmv$count == 0, 0, 1)
all_cbcl_gmv$health <- as.factor(all_cbcl_gmv$health)

smri_list <- colnames(all_cbcl_gmv %>% select(contains("smri")))
smri_list

for (smri in smri_list) {
  print(smri)
  print(ggplot(all_cbcl_gmv, aes_string(smri, fill = "health"))
   + geom_density(position = "identity", alpha = 0.5))
}
```






# Cortical Thickness
```{r}
bm_cortthick_cbcl_t_bin <- as.data.frame(bm_cortthick_cbcl_t_bin)
bm_cortthick_cbcl_t_bin$count <- rowSums(bm_cortthick_cbcl_t_bin == 1)

healthy_cbcl_cortthick <- bm_cortthick_cbcl_t_bin[which(bm_cortthick_cbcl_t_bin$count == 0), ]
unhealthy_cbcl_cortthick <- bm_cortthick_cbcl_t_bin[which(bm_cortthick_cbcl_t_bin$count != 0), ]


nrow(healthy_cbcl_cortthick) # 4395
nrow(unhealthy_cbcl_cortthick) # 988

write.csv(bm_cortthick_cbcl_t_bin, "/Users/hansoochang/Drexel/ABCD/data/bm_cortthick_cbcl_67.csv")
write.csv(healthy_cbcl_cortthick, file = "/Users/hansoochang/Drexel/ABCD/data/healthy_cbcl_cortthick_67.csv")
write.csv(unhealthy_cbcl_cortthick, "/Users/hansoochang/Drexel/ABCD/data/unhealthy_cbcl_cortthick_67.csv")
```






