---
title: "PhysHealth"
output: html_document
date: "2023-01-20"
---

# Physical health (did they go to the hospital for x) for 1-3 year time point. Baseline timepoint is in a different csv file. 
```{r}
phys <- read.csv("/Users/hansoochang/Drexel/ABCD/data/abcd_lpmh01.csv")
phys <- phys[-1,]

head(phys)
skim(phys)
```



# Get only columns I want and split into collection timepoints
Take out medical conditions like head injury that results from some external force.
```{r}
phys <- phys[, c(4,8,9,12,15:19,21,23:24,26:28,63)]
phys <- select(phys, -contains(c("times", "notes")))

phys_1 <- phys[which(phys$eventname == "1_year_follow_up_y_arm_1"), ]
phys_2 <- phys[which(phys$eventname == "2_year_follow_up_y_arm_1"), ]
phys_3 <- phys[which(phys$eventname == "3_year_follow_up_y_arm_1"), ]


```


# Remove missing cases
The empty values in the dataframe seem to indicate "0" or not applicable
```{r}
phys_1 <- replace(phys_1, phys_1=='', NA)
nrow(phys_1) # 11225
nrow(phys_1[complete.cases(phys_1),]) # 10825
phys_1 <- phys_1[complete.cases(phys_1),]

phys_2 <- replace(phys_2, phys_2=='', NA)
nrow(phys_2) # 10414
nrow(phys_2[complete.cases(phys_2),]) # 6274
phys_2 <- phys_2[complete.cases(phys_2),]

phys_3 <- replace(phys_3, phys_3=='', NA)
nrow(phys_3) # 6251
nrow(phys_3[complete.cases(phys_3),]) # 2108
phys_3 <- phys_3[complete.cases(phys_3),]

```


# Merge with Biomarkers cohort
## Bio Age
```{r}
bm <- read.csv("/Users/hansoochang/Drexel/ABCD/data/biomarkers.csv")

bm_phys_2 <- merge(bm, phys_2, by.x = c("subjectkey"), by.y =
                   c("subjectkey"))

length(unique(phys_2$subjectkey))
length(phys_2$subjectkey)

head(bm_phys_2)
nrow(bm_phys_2)
```
Since there are only 273 participants who have both biomarker data and phys health data, let's try looking at phys health from the previous timepoint. 

```{r}
bm_phys_1 <- merge(bm, phys_1, by.x = c("subjectkey"), by.y =
                   c("subjectkey"))

head(bm_phys_1)
nrow(bm_phys_1)
```
It seems that at timepoint 1, the sample size is much larger. We can use some of these timepoints to fill in the missing information.

## Brain Age
### GMV
Only for year 2 timepoint for both brain age bms and physical data
```{r}
### Desikan Parcellation
brain <- read.csv("/Users/hansoochang/Drexel/ABCD/data/smrip_gmv_y2.csv")

brain_phys_2 <- merge(brain, phys_2, by = c("subjectkey", "eventname"))

head(brain_phys_2)
nrow(brain_phys_2) # 4370



### Destrieux Parcellation 
# brain <- read.csv("/Users/hansoochang/Drexel/ABCD/data/stand_dest_vol_y2.csv")
# 
# brain_phys_2 <- merge(brain, phys_2, by = c("subjectkey", "eventname"))
# 
# head(brain_phys_2)
# nrow(brain_phys_2) # 4818
```

### Cortical Thickness
```{r}
### Desikan Parcellation
cortthick <- read.csv("/Users/hansoochang/Drexel/ABCD/data/smrip_cortthick_y2.csv")

cortthick_phys_2 <- merge(cortthick, phys_2, by = c("subjectkey", "eventname"))

head(cortthick_phys_2)
nrow(cortthick_phys_2) # 4117
```



## Get phys prob for brain age
### GMV
```{r}
brain_phys_2$PhysProb <- 
  ifelse(rowSums(as.data.frame(apply(brain_phys_2 
                                     %>% select(contains("medhx")), 2, as.numeric))) > 0, 1, 0)


write.csv(brain_phys_2, "/Users/hansoochang/Drexel/ABCD/data/brain_phys_2")
```

### Cortical Thickness
```{r}
cortthick_phys_2$PhysProb <- 
  ifelse(rowSums(as.data.frame(apply(cortthick_phys_2 
                                     %>% select(contains("medhx")), 2, as.numeric))) > 0, 1, 0)


write.csv(cortthick_phys_2, "/Users/hansoochang/Drexel/ABCD/data/cortthick_phys_2")
```




# Merge Bio Age BM's with year 2 phys and if any missing, then year 1 phys
```{r}
bm_phys_2_left <- merge(bm, phys_2, by = c("subjectkey"), all.x = T)

# Get incomplete cases for merging phys_2 and bm at year 2
bm_phys_2_left_inc <- bm_phys_2_left[!complete.cases(bm_phys_2_left),]
bm_inc_ind <- bm_phys_2_left_inc[, -c(39:51)]

# final phys_1 and bm_2 merge
bm_phys_2_1 <- merge(bm_inc_ind, phys_1, by = c("subjectkey"))

# bind phys_1 and bm_2 merge and phys_2 and bm at year 2
bm_2_phys_2_1 <- rbind(bm_phys_2_left[complete.cases(bm_phys_2_left),][,-c(37:38)], 
                       bm_phys_2_1[,-c(37:40)]) 

bm_2_phys_2_1[,c(37:49)] <- as.numeric(unlist(bm_2_phys_2_1[,c(37:49)]))

bm_2_phys_2_1$PhysProb <- ifelse(rowSums(bm_2_phys_2_1[,c(37:49)]) > 0, 1, 0)
skim(bm_2_phys_2_1)

write.csv(bm_2_phys_2_1, "/Users/hansoochang/Drexel/ABCD/data/bm_2_phys_2_1")

```

# Look at any children who are on medications
```{r}
medsy <- read.delim("/Users/hansoochang/Drexel/ABCD/data/medsy01.txt")
medsy <- medsy[-1, ]
```

Get only columns that I want
```{r}

# We just want to know if the child is taking any medications, and perhaps which ones.
medsy_1 <- medsy[, c(4,9:10, 296)]

medsy_1
```
0 = Yes; 1 = Yes; 2 = Refused - Record reason for refusal in Comments Section Se negó - anote el motivo por el cual se negó en la sección de Comentarios.; 3 = Took No Medications No usó ningún medicamento | Mark the form status as 'Unverified' if you are waiting on the parent to provide child's medications.//The ABCD Study will be describing all medications its participants are using, both prescription and over-the-counter. These include pills, liquid medications; skin patches, eye drops, creams, salves, inhalers and injections, as well as cold or allergy medications, vitamins, herbal remedies and other supplements

```{r}
table(medsy_1$brought_medications)
table(medsy_1[medsy_1$eventname == "baseline_year_1_arm_1",]$brought_medications)
medsy_1[which(medsy_1$brought_medications == 4), ]
```


# Split into healthy and unhealthy
## Bio Age
```{r}
healthy_phys <- bm_2_phys_2_1[which(bm_2_phys_2_1$PhysProb == 0), ]
unhealthy_phys <- bm_2_phys_2_1[which(bm_2_phys_2_1$PhysProb == 1), ]

nrow(healthy_phys) # 568
nrow(unhealthy_phys) # 85

write.csv(healthy_phys, "/Users/hansoochang/Drexel/ABCD/data/healthy_phys")
write.csv(unhealthy_phys, "/Users/hansoochang/Drexel/ABCD/data/unhealthy_phys")

```


## Brain Age
### GMV
```{r}
healthy_brain_phys <- brain_phys_2[which(brain_phys_2$PhysProb == 0), ]
unhealthy_brain_phys <- brain_phys_2[which(brain_phys_2$PhysProb == 1), ]

nrow(healthy_brain_phys) # 3809
nrow(unhealthy_brain_phys) # 561

write.csv(healthy_brain_phys, "/Users/hansoochang/Drexel/ABCD/data/healthy_brain_phys")
write.csv(unhealthy_brain_phys, "/Users/hansoochang/Drexel/ABCD/data/unhealthy_brain_phys")
```

### Cortical Thickness
```{r}
healthy_cortthick_phys <- cortthick_phys_2[which(cortthick_phys_2$PhysProb == 0), ]
unhealthy_cortthick_phys <- cortthick_phys_2[which(cortthick_phys_2$PhysProb == 1), ]

nrow(healthy_cortthick_phys) # 3711
nrow(unhealthy_cortthick_phys) # 559


write.csv(healthy_cortthick_phys, "/Users/hansoochang/Drexel/ABCD/data/healthy_cortthick_phys")
write.csv(unhealthy_cortthick_phys, "/Users/hansoochang/Drexel/ABCD/data/unhealthy_cortthick_phys")
```



## Bio Age Phys Problems
```{r}
colnames(bm_2_phys_2_1)
sort(colSums(bm_2_phys_2_1[,c(37:50)]))

```
From most common:
1. Problems with Vision - 77 XXX
2. Asthma - 44
3. Very Bad Headaches - 24
4. Hearing Problem - 13 XXX
5. Bronchitis - 11
6. Heart Problems - 8
7. Diabetes - 7
8. Epilepsy/seizures - 4
9. Sickle Cell Anemia - 2
10. Multiple Sclerosis - 2
11. Muscular Dystrophy - 2
12. Kidney Disease - 2
13. Cerebral Palsy - 2
14. Cancer/Leukemia - 2
15. Seizure/Convulsion - 0

## Brain Age Phys Problems
### GMV
```{r}
colnames(brain_phys_2)
brain_phys_2[,c(6:97, 99:112)] <- as.data.frame(apply(brain_phys_2[,c(6:97, 99:112)], 2, as.numeric))
sort(colSums(brain_phys_2[,c(99:112)]))


```
1. A

### Cortical Thickness
```{r}
colnames(cortthick_phys_2)
cortthick_phys_2[,c(6:112, 115:128)] <- as.data.frame(apply(cortthick_phys_2[,c(6:112, 115:128)], 2, as.numeric))
sort(colSums(brain_phys_2[,c(115:128)]))

```















