---
title: "PhysHealth_5.0"
output: html_document
date: "2023-07-18"
---

This file separates unhealthy from healthy participants by physical health. This file does not merge biomarkers or GMV.


# Libraries
```{r, warning=FALSE, error = FALSE, message=FALSE}
library(BioAge)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(Metrics)
library(stats)
library(skimr)
library(stringr)
library(devtools)
library(neuroCombat)
library(tidyr)
library(reshape2)
```


# Read in Data
```{r}
# Child medical history
mhx <- read.csv(paste0(root,"abcd-data-release-5.1/core/physical-health/ph_p_mhx.csv"))

```


# Filter by relevant columns
```{r}
mhx <- mhx %>% select(src_subject_id, eventname, medhx_2a:medhx_2q, medhx_6h, 
                               medhx_6l, medhx_6p, medhx_11, medhx_12, medhx_2a_l:medhx_2q_l, medhx_6h_l, 
                               medhx_6l_l, medhx_6p_l, medhx_11_l, medhx_12_l)

# Reverse medhx_11, medhx_12, medhx_11_l, medhx_12_l (Yes is healthy)
mhx <- mhx %>%
  mutate_at(vars(medhx_11, medhx_12, medhx_11_l, medhx_12_l), ~recode(., `0` = 1, `1` = 0))

mhx %>% mutate_at(vars(medhx_2a:medhx_12_l), as.factor) %>% skim()
```

Columns ending with _l are for follow-up time points. Baseline results have their own columns


# Find all rows with a significant physical health problem
NB: Take out vision problems, hearing problems
```{r}
mhx <- mhx %>% select(-c(medhx_2n, medhx_2n_l, medhx_2i, medhx_2i_l))

# Binary column if participant has any problem
mhx$phys_health_bin <- ifelse(rowSums(mhx %>% select(-c(src_subject_id, eventname)) >= 1, 
                                  na.rm = TRUE) > 0, 1, 0)

# Total number of problems by row
tot_prob <- rowSums(mhx %>% select(medhx_2a:medhx_12_l), na.rm = T)
mhx$tot_prob <- tot_prob

table(mhx %>% filter(eventname == "baseline_year_1_arm_1") %>% select(tot_prob))
```


# Visualize
```{r}
column_sums <- colSums(mhx %>% select(medhx_2a:medhx_12_l), na.rm = T)

columns_sums_base <- colSums(mhx %>% filter(eventname == "baseline_year_1_arm_1") %>% 
                               select(medhx_2a:medhx_12_l), na.rm = T)
sort(columns_sums_base)
```
Top are
1. allergies (baseline)
2. High fever (baseline)
3. allergies (follow-up)
4. asthma (baseline)
5. asthma (follow-up)
6. high-fever (follow_up)
7. bronchitis (baseline)

# Export
```{r}
write.csv(mhx, paste0(root, "Version5.0_Exported_Data/mhx.csv"))
```



